---
title: "process_commuters"
output: html_document
---

# Frontmatter
Read libraries
```{r}
library(tidyverse)
library(sf)
library(tmap)
library(readxl)
library(matsim)
```

inputs and outputs
```{r}
in_jis_shp <- "../shared-svn/projects/matsim-gunma/data/processed/01_shapefiles/jis_zones/jis_zones.shp"
in_commuter_census <- "../shared-svn/projects/matsim-gunma/data/raw/2020census/e06_02-01.xlsx"
```

Function to rescale commuter df, to have a new total number of commuters
```{r}

scale_counts_exact <- function(df, target, col = "n") {
  x <- df[[col]]
  w <- x * target / sum(x)

  base <- floor(w)
  rem <- target - sum(base)

  idx <- order(w - base, decreasing = TRUE)[seq_len(rem)]

  scaled <- base
  scaled[idx] <- scaled[idx] + 1

  df[[paste0(col, "_scaled")]] <- scaled
  df
}
```


work with shape files 
```{r}

jis_zones_shp <- st_read(in_jis_shp)

gunma_shp <- jis_zones_shp %>%  filter(str_starts(id, "10")) %>% summarise()

env00 <- gunma_shp %>% st_bbox() %>% st_as_sfc()

env50 <- st_buffer(gunma_shp, dist = 50000)  %>% st_bbox() %>% st_as_sfc()

env75 <- st_buffer(gunma_shp, dist = 75000)  %>% st_bbox() %>% st_as_sfc()

env100 <- st_buffer(gunma_shp, dist = 100000)  %>% st_bbox() %>% st_as_sfc()

jis_100 <- jis_zones_shp %>% st_filter(env100)

tmap_mode("view")
tm_shape(env50)+ tm_borders() +
  tm_shape(jis_100)+ tm_borders() +
  tm_shape(gunma_shp) +
  tm_polygons(fill = "blue")


```

Read Census Data
```{r}
commuters <- read_excel(in_commuter_census, skip = 7)

commuters_cleaned <- commuters %>% 
  rename(from = "...4") %>% 
  select(!starts_with("...")) %>%
  slice(-(1:2)) %>% 
  pivot_longer(cols = -from,names_to = "to",values_to = "n") %>% 
    separate_wider_delim(from, delim = "_", names = c("from",NA)) %>% 
    separate_wider_delim(to, delim = "_", names = c("to",NA)) %>% 
  mutate(n = as.numeric(n)) %>% 
  drop_na(n)
```

## Exploratory Analysis

### COMMUTERS TO GUNMA
93% of work trip ending to Gunma, are from residents living in Gunma. 7% are from outside
56557 people coming into Gunma for work

Within the 100km envelope, we have 55890 commuters (99%)
Within the 75km envelope, we have 55365 commuters (98%)
Within the 50km envelope, we have 54172 commuters (96%)
```{r}
commuters_cleaned %>%  
  filter(from %in% c("00000","10000") & to == "10000") 


# prep dataframe
commuters_to_gunma <- commuters_cleaned %>% 
  filter(to == "10000") %>% 
  filter(!str_ends(from, "00")) %>% 
  filter(!str_starts(from, "10")) %>% 
  # mutate(id = paste0('"', from, '"')) %>% 
    mutate(id = from) %>% 
  right_join(jis_100, by = "id") %>% 
  st_as_sf() %>% 
  filter(!str_starts(id, "10")) %>% 
  replace_na(list(n = 0))

# how many commuters are contained within the 100km envelope (including municipalities that extend past the 100km mark)
commuters_to_gunma %>%  st_filter(env100,.predicate = sf::st_within) %>% st_drop_geometry() %>%  summarise(n = sum(n))
# how many commuters are contained within the 75km envelope (including municipalities that extend past the 50km mark)
commuters_to_gunma %>% st_filter(env75,.predicate = sf::st_within) %>% st_drop_geometry() %>%  summarise(n = sum(n))
# how many commuters are contained within the 50km envelope (including municipalities that extend past the 50km mark)
commuters_to_gunma %>% st_filter(env50,.predicate = sf::st_within) %>% st_drop_geometry() %>%  summarise(n = sum(n))
  
tmap_mode("plot")
tm_basemap("Esri.WorldGrayCanvas") + 
tm_shape(commuters_to_gunma) +
  tm_polygons(
    color = NA,
    fill = "n",
    breaks = c(0,1,5,10,50,100,500,1000,5000),
    lwd = 0
  ) + tm_shape(env75)+ tm_borders(col = "#B32928", lwd = 4) +
  tm_shape(gunma_shp) +
  tm_polygons(fill = "#8425F4") +
  tm_title("Commuters To Gunma Prefecture")

  # select(id,n) %>% view()
  # write_csv("../shared-svn/projects/matsim-gunma/data/processed/census/commuters_to_gunma_jis.csv")


# commuters_cleaned %>% 
#   filter(str_ends(from, "000") & from != "00000" & from !="10000" & to == "10000") %>% separate_wider_position(from,c(from = 2, 3))  %>%
#   mutate(from = factor(as.numeric(from),levels = seq(1:47),labels = prefectures_ordered_by_code)) %>%  
#   arrange(n) %>% 
# ggplot() + geom_col(aes(from,n)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Commuters TO Gunma")
```


### COMMUTERS FROM GUNMA
91% of work trip starting in Gunma, are from residents living in Gunma. 9% go outside
79371 commuters of which 52246 had known destinations (not code 99998 or 99999)
within 100km :51223 (98% of known)
within 75km: 50681 (97% of known)
within 50km 49528 (95% of known)



```{r}

commuters_cleaned %>%  
  filter(to %in% c("00000","10000") & from == "10000") 




commuters_from_gunma <- commuters_cleaned %>% 
  filter(from == "10000") %>% 
  filter(!str_ends(to, "00")) %>% 
  filter(!str_starts(to, "10")) %>% 
  filter(!str_starts(to,"9999")) %>% 
  mutate(id = to) %>% 
  # mutate(id = paste0('"', to, '"')) %>% 
  right_join(jis_100, by = "id") %>%
  st_as_sf() %>% 
  filter(!str_starts(id, "10")) %>% 
  replace_na(list(n = 0))


# how many commuters are contained within the 100km envelope (including municipalities that extend past the 100km mark)
commuters_from_gunma %>% st_filter(env100,.predicate = sf::st_within)%>% st_drop_geometry() %>%  summarise(n = sum(n))
# how many commuters are contained within the 75km envelope (including municipalities that extend past the 75km mark)
commuters_from_gunma %>% st_filter(env75,.predicate = sf::st_within) %>% st_drop_geometry() %>%  summarise(n = sum(n))# how many commuters are contained within the 50km envelope (including municipalities that extend past the 50km mark)
commuters_from_gunma %>% st_filter(env50,.predicate = sf::st_within) %>% st_drop_geometry() %>%  summarise(n = sum(n))
  

tmap_mode("plot")
tm_basemap("Esri.WorldGrayCanvas") + 
tm_shape(commuters_from_gunma) +
  tm_polygons(
    color = NA,
    fill = "n",
    breaks = c(0,1,5,10,50,100,500,1000,5000),
    lwd = 0
  ) + tm_shape(env75)+ tm_borders(col = "#B32928", lwd = 4) +
  tm_shape(gunma_shp) +
  tm_polygons(fill = "#8425F4") +
  tm_title("Commuters From Gunma Prefecture")


```

## Produce output/input for MATSim generation of MATSim Commuter

Reassign commuters with origins/destinations outside of the 75km study area back to municipalities within the zone. 
```{r}

# Scale commuters to gunma
commuters_to_gunma_target <- 56557
commuters_to_gunma_75_prep <- commuters_cleaned %>% 
  filter(str_starts(to,"10")) %>% 
  filter(!str_ends(to, "00")) %>% 
  filter(!str_ends(from, "00")) %>% 
  filter(!str_starts(from, "10")) %>% 
  # mutate(id = paste0('"', from, '"')) %>% 
    mutate(id = from) %>% 
  right_join(jis_100, by = "id") %>% 
  st_as_sf() %>% 
  replace_na(list(n = 0))  %>% 
  st_filter(env75,.predicate = sf::st_within) %>%   st_drop_geometry()


commuters_to_gunma_75_scaled <- scale_counts_exact(commuters_to_gunma_75_prep,commuters_to_gunma_target)

commuters_to_gunma_75_scaled %>% summarise(n = sum(n),n_scaled = sum(n_scaled))


# Scale commuters from gunma
commuters_from_gunma_target <- 52246
commuters_from_gunma_75_prep <- commuters_cleaned %>% 
  filter(str_starts(from,"10")) %>% 
  filter(!str_ends(from, "00")) %>% 
  filter(!str_ends(to, "00")) %>% 
  filter(!str_starts(to, "10")) %>% 
  # mutate(id = paste0('"', from, '"')) %>% 
    mutate(id = to) %>% 
  right_join(jis_100, by = "id") %>% 
  st_as_sf() %>% 
  replace_na(list(n = 0))  %>% 
  st_filter(env75,.predicate = sf::st_within) %>%   st_drop_geometry()

commuters_from_gunma_75_scaled <- scale_counts_exact(commuters_from_gunma_75_prep,commuters_from_gunma_target)

commuters_from_gunma_75_scaled %>% summarise(n = sum(n), n_scaled = sum(n_scaled))


# Filter trips within gunma 

commuters_within_gunma <- commuters_cleaned %>% 
  filter(str_starts(from, "10")) %>% 
  filter(str_starts(to, "10")) %>%
  filter(!str_ends(from, "00")) %>% 
  filter(!str_ends(to, "00")) %>% 
  replace_na(list(n = 0)) 

# 767943 trips within gunma
commuters_within_gunma %>% summarise(n = sum(n))

# 6176 trips with code 99998 + and 21241 trips with 99999(unknown/foreign)
commuters_cleaned %>% filter(from == "10000") %>% filter(str_starts(to,"9999"))
commuters_within_gunma_target <- 767943 + 6176 + 21241


# scale
commuters_within_gunma_scaled <- scale_counts_exact(commuters_within_gunma,commuters_within_gunma_target)

commuters_within_gunma_scaled %>% summarise(n_scaled = sum(n_scaled))



# combine all three subpopulations:
commuters_scaled_combined <- bind_rows(commuters_within_gunma_scaled, commuters_from_gunma_75_scaled %>% select(-id), commuters_to_gunma_75_scaled %>% select(-id))

# sanity check
# total is 903984
commuters_scaled_combined %>% drop_na(from,to) %>% summarise(n = sum(n), n_scaled = sum(n_scaled))


# total = 824500 + 847314 - 767943 = 903871
# about 113 off, due to rounding errors, but I think this good enough...
commuters_cleaned %>% filter((from == "00000" & to == "10000") | (from == "10000" & to == "00000") | (from == "10000" & to == "10000"))


commuters_scaled_combined %>% select(-n) %>% drop_na(from,to) %>% 
write_csv("../shared-svn/projects/matsim-gunma/data/processed/commuters_od_matrix/work_od_matrix_scaled.csv")



```




Create reference file for Activities Dashboard

includes work activities in Gunma, originating from anywhere in the country

id,count,relative_density,density,area
```{r}

# jp_shp <- st_read("../shared-svn/projects/matsim-gunma/data/raw/shp/nationwide_municip_2020/N03-20_200101.shp") %>% select(id = N03_007) %>% st_transform(2450) %>% mutate(area = as.numeric(st_area(.))) %>% st_drop_geometry() %>% group_by(id) %>% summarise(area = sum(area))

area_per_municipality <- jis_zones_shp %>%  mutate(area = as.numeric(st_area(.))) %>% st_drop_geometry() %>% group_by(id) %>% summarise(area = sum(area))


commuters_cleaned %>%
  filter(from %in% c("00000")) %>% 
  filter(!str_ends(to,"00")) %>% 
  filter(str_starts(to,"10")) %>% 
  select(id = to, count = n) %>% 
  left_join(area_per_municipality) %>% 
  mutate(area = area / 1000 / 1000) %>% 
  mutate(density = count / area) %>% 
  mutate(relative_density = density / mean(density, na.rm = TRUE)) %>% 
  mutate(id = paste0('"', id, '"')) %>%
  # mutate(id = as.numeric(id)) %>% 
  write_csv("resources/activities_work_per_region-ref.csv")


  

```



## Produce Sim/Ref Files for AggrOD Dashboard
MATSim Output
```{r}

sample_multiplier <- 4

output_persons <- read_delim("output/eval.output_persons.csv.gz") 

output_trips <- read_delim(
  "output/eval.output_trips.csv.gz", delim = ";"
)

# sim
od_sim <- output_trips %>% 
  filter(end_activity_type == "work") %>% 
  group_by(person) %>% 
  summarise(end_x = first(end_x), end_y = first(end_y)) %>% 
  st_as_sf(coords = c("end_x","end_y"), crs=2450) %>% 
  st_join(jis_zones_shp) %>%
  st_drop_geometry() %>% 
  left_join(output_persons %>% select(person,zone), by = "person") %>% 
  select(person, from = zone, to = id) %>%  
  # mutate(from = sprintf('%05d', from)) %>% 
  # mutate(to = str_remove_all(to,'"')) %>%
  group_by(from,to) %>% 
  summarise(n_sim = sample_multiplier * n()) 
# for 25% sample

# ref
#str_ends(from, "000") & from != "00000" & from !="10000" & to == "10000"
od_ref <- commuters_cleaned %>% 
  filter(str_starts(to,"10") | str_starts(from,"10")) %>% 
  filter(!str_ends(from,"00")) %>% 
  filter(!str_ends(to,"00")) %>% 
  filter(!str_starts(to,"9999")) %>% 
  # mutate(from = as.numeric(from), to = as.numeric(to)) %>% 
  rename(n_ref = n)



od_comb <- full_join(od_ref,od_sim) %>% 
  replace_na(list(n_ref = 0, n_sim = 0)) %>% 
  mutate(diff = n_sim - n_ref) %>% 
  mutate(pct_diff = diff/n_ref * 100) %>% 
  arrange(-n_ref) 


# TAB 1: WITHIN GUNMA 
od_comb_gunma_only <- od_comb %>% filter(str_starts(from, "10"),str_starts(to, "10"))

# sim
od_comb_gunma_only %>% 
  select(from,to,n_sim) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_od_sim.csv", delim = ";")

#ref
od_comb_gunma_only %>% 
  select(from,to,n_ref) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_od_ref.csv", delim = ";")

#diff
od_comb_gunma_only %>% 
  mutate(diff = abs(diff)) %>% 
  select(from,to,diff) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_od_diff.csv", delim = ";")
  

# TAB 2a: Now the commuter flows to Gunma (on Municipality level)

od_comb_outside_gunma_inflow <- od_comb %>% 
  filter(!str_starts(from,"10") & str_starts(to, "10"))

# sim
od_comb_outside_gunma_inflow %>% 
  select(from,to,n_sim) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_inflow_od_sim.csv", delim = ";")

#ref
od_comb_outside_gunma_inflow %>% 
  select(from,to,n_ref) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_inflow_od_ref.csv", delim = ";")

#diff
od_comb_outside_gunma_inflow %>% 
  mutate(diff = abs(diff)) %>% 
  select(from,to,diff) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_inflow_od_diff.csv", delim = ";")


# TAB 2b: Now the commuter flows to Gunma (on Municipality level)


od_comb_outside_gunma_outflow <- od_comb %>% 
  filter(str_starts(from,"10") & !str_starts(to, "10")) 

# sim
od_comb_outside_gunma_outflow %>% 
  select(from,to,n_sim) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_outflow_od_sim.csv", delim = ";")

#ref
od_comb_outside_gunma_outflow %>% 
  select(from,to,n_ref) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_outflow_od_ref.csv", delim = ";")

#diff
od_comb_outside_gunma_outflow %>% 
  mutate(diff = abs(diff)) %>% 
  select(from,to,diff) %>%
  filter(from !=to) %>%
  write_delim("resources/gunma_outflow_od_diff.csv", delim = ";")

# TAB 3: Now on a prefecture level

od_comb_outside_gunma_pref <- od_comb %>% 
  separate_wider_position(from, widths = c("from" = 2, 3)) %>% 
  separate_wider_position(to, widths = c("to" = 2, 3)) %>%
  group_by(from,to) %>% summarise(n_ref = sum(n_ref), n_sim = sum(n_sim)) %>% 
  mutate(diff = n_sim-n_ref) %>% 
  filter(from !=to)

# 3a: inflow

od_comb_outside_gunma_pref_inflow <- od_comb_outside_gunma_pref %>%
  filter(to == "10")

# sim
od_comb_outside_gunma_pref_inflow %>% 
  select(from,to,n_sim) %>%
  write_delim("resources/gunma_inflow_pref_od_sim.csv", delim = ";")

#ref
od_comb_outside_gunma_pref_inflow %>% 
  select(from,to,n_ref) %>%
  write_delim("resources/gunma_inflow_pref_od_ref.csv", delim = ";")

#diff
od_comb_outside_gunma_pref_inflow %>% 
  mutate(diff = abs(diff)) %>% 
  select(from,to,diff) %>%
  write_delim("resources/gunma_inflow_pref_od_diff.csv", delim = ";")

# 3b: outflow

od_comb_outside_gunma_pref_outflow <- od_comb_outside_gunma_pref %>%
  filter(from == "10")

# sim
od_comb_outside_gunma_pref_outflow %>% 
  select(from,to,n_sim) %>%
  write_delim("resources/gunma_outflow_pref_od_sim.csv", delim = ";")

#ref
od_comb_outside_gunma_pref_outflow %>% 
  select(from,to,n_ref) %>%
  write_delim("resources/gunma_outflow_pref_od_ref.csv", delim = ";")

#diff
od_comb_outside_gunma_pref_outflow %>% 
  mutate(diff = abs(diff)) %>% 
  select(from,to,diff) %>%
  write_delim("resources/gunma_outflow_pref_od_diff.csv", delim = ";")

# and now the filtered prefecture shape file


prefectures_shp <- jis_zones_shp %>% st_filter(env100) %>%  separate_wider_position(id, widths = c("id" = 2,  3)) %>% st_as_sf() %>% group_by(id) %>% summarise() %>% st_simplify()

prefectures_shp %>% tm_shape() + tm_polygons()

# prefectures_shp %>% tm_shape() + tm_polygons()

# prefectures_shp %>%  st_write("resources/pref_shp.shp")

# matsim_output <- gunma_shp %>% 
#   st_join(output_trips %>% st_as_sf(coords = c("end_x","end_y"), crs = 2450) %>% filter(end_activity_type == "work")) %>% 
#   group_by(N03_007) %>% 
#   count() %>% 
#   mutate(n = n * 100)

# jenks binning
# compare origins as well.
# average trip length & distribution
# tm_shape(matsim_output)+tm_polygons(fill = "n", breaks = c(seq(0,150000,10000),Inf))+ tm_title("MATSim Output")

# destinations_data %>% st_drop_geometry() %>% full_join(matsim_output, by = "NAME_2") %>% mutate(diff = n.x - n.y) %>% st_as_sf() %>%  tm_shape()+tm_polygons(fill = "diff") + tm_title("Original Data - MATSim Output")
```


# Deprecated

Education
```{r}
edu_commuters <- read_excel("../shared-svn/projects/matsim-gunma/data/raw/2020census/e06_03-01.xlsx", skip = 7)


edu_commuters_cleaned <- edu_commuters %>% 
  rename(from = "...4") %>% 
  select(!starts_with("...")) %>%
  slice(-(1:2)) %>% 
  pivot_longer(cols = -from,names_to = "to",values_to = "n") %>% 
    separate_wider_delim(from, delim = "_", names = c("from",NA)) %>% 
    separate_wider_delim(to, delim = "_", names = c("to",NA)) %>% 
  mutate(n = as.numeric(n)) %>% 
  drop_na(n)


edu_commuters_cleaned %>%
  filter(from %in% c("00000")) %>% 
  filter(!str_ends(to,"00")) %>% 
  filter(str_starts(to,"10")) %>% 
  select(id = to, count = n) %>% 
  left_join(jp_shp) %>% 
  mutate(area = area / 1000 / 1000) %>% 
  mutate(density = count / area) %>% 
  mutate(relative_density = density / mean(density, na.rm = TRUE)) %>% 
  mutate(id = paste0('"', id, '"')) %>%
  # mutate(id = as.numeric(id)) %>% 
  write_csv("resources/activities_education_per_region-ref.csv")
```



```{r}
commuters_cleaned %>% 
  filter(from %in% gunma_shp$N03_007 & to %in% gunma_shp$N03_007) %>%
  group_by(to) %>% 
  summarize(n = sum(n)) %>%
  left_join(gunma_shp, by = c("to" = "N03_007")) %>% 
  st_as_sf() %>%
  tm_shape() + tm_polygons(fill = "n", breaks = c(seq(0,150000,10000),Inf)) + tm_title("Census Data")
  
```


gunma_shp
```{r}
district_dict <- data.frame(
  district_jp = c(
    "前橋市", "高崎市", "桐生市", "伊勢崎市", "太田市",
    "沼田市", "館林市", "渋川市", "藤岡市", "富岡市",
    "安中市", "みどり市", "北群馬郡", "多野郡", "甘楽郡",
    "吾妻郡", "利根郡", "佐波郡", "邑楽郡"
  ),
  district_en = c(
    "Maebashi City", "Takasaki City", "Kiryu City", "Isesaki City", "Ota City",
    "Numata City", "Tatebayashi City", "Shibukawa City", "Fujioka City", "Tomioka City",
    "Annaka City", "Midori City", "Kitagunma District", "Tano District", "Kanra District",
    "Agatsuma District", "Tone District", "Sawa District", "Ora District"
  ),
  stringsAsFactors = FALSE
)

gunma_shp <- st_read("../shared-svn/projects/matsim-gunma/data/raw/shp/gunma_municip_2020/N03-20200101_10_GML/N03-20_10_200101.shp",options = "ENCODING=CP932")  %>% mutate(district_jp = case_when(is.na(N03_003)~ N03_004, .default = N03_003)) %>% left_join(district_dict) %>% st_transform(2450) 

# prefecture codes / dictionary
# prefecture_codes <- st_read("../shared-svn/projects/matsim-gunma/data/raw/shp/jp_2450/jp_2450.shp") %>% glimpse() %>% st_drop_geometry() %>% select(ID_1, NAME_1)


prefectures_ordered_by_code <- c(
  "Hokkaido",
  "Aomori",
  "Iwate",
  "Miyagi",
  "Akita",
  "Yamagata",
  "Fukushima",
  "Ibaraki",
  "Tochigi",
  "Gunma",
  "Saitama",
  "Chiba",
  "Tokyo",
  "Kanagawa",
  "Niigata",
  "Toyama",
  "Ishikawa",
  "Fukui",
  "Yamanashi",
  "Nagano",
  "Gifu",
  "Shizuoka",
  "Aichi",
  "Mie",
  "Shiga",
  "Kyoto",
  "Osaka",
  "Hyogo",
  "Nara",
  "Wakayama",
  "Tottori",
  "Shimane",
  "Okayama",
  "Hiroshima",
  "Yamaguchi",
  "Tokushima",
  "Kagawa",
  "Ehime",
  "Kochi",
  "Fukuoka",
  "Saga",
  "Nagasaki",
  "Kumamoto",
  "Oita",
  "Miyazaki",
  "Kagoshima",
  "Okinawa"
)

```


```{r}

commuters_cleaned %>% 
  filter(str_ends(to, "000") & to != "00000" & to !="10000" & from == "10000") %>% separate_wider_position(to,c(to = 2, 3))  %>%
  mutate(to = factor(as.numeric(to),levels = seq(1:47),labels = prefectures_ordered_by_code)) %>%  
  arrange(n) %>% 
ggplot() + geom_col(aes(to,n)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) + labs(title = "Commuters FROM Gunma")

```

