---
title: "proces_travel_survey2"
output: html_document
date: "2026-02-10"
---

This script is adapted from Dr. Lichen LUO 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Frontmatter
Libraries
```{r}
library(data.table)
library(stringr)
library(plyr)
library(dplyr)
# library(rgdal)
library(sp)
library(sf)
library(stringi)
library(readr)
```
# Lichen's Wrangling & Filtering 

Read Input data
```{r}
df_raw<-fread("../shared-svn/projects/matsim-gunma/data/raw/travel_survey/pt.csv")
setnames(df_raw, c("レコード区分",	"票区分",	"回収分類",	"バッチ番号",	"整理番号小ゾーン",	"整理番号世帯SEQ",	"世帯人数",	"調査年次",	
                    "現住所", "現住所「番」「番地」",	"現住所「号」",	"所有車両軽乗用車",	"所有車両乗用車",	"所有車両軽貨物車",	"所有車両貨物自動車",
                    "所有車両自転車",	"所有車両原動機付自転車",	"所有車両自動二輪車",	"個人番号",	"世帯票性別",	"世帯票年齢",	"職業",	"就業形態",
                    "勤務先・通学先・通園先の所在地",	"勤務先・通学先・通園先の所在地「番」「番地」",	"勤務先・通学先・通園先の所在地「号」",
                    "外出の際の付き添い",	"保有運転免許①",	"保有運転免許②", "自由に使える自動車", "調査日月", "調査日日","トリップ有無",
                    "トリップ数","トリップ番号",	"出発地区分",	"出発地ゾーン",	"出発地「番」「番地」",	"出発地「号」",	"出発地施設の種類",
                    "出発時刻午前・午後・翌午前",	"出発時刻時",	"出発時刻分",	"到着地区分",	"到着地ゾーン",	"到着地「番」「番地」", 
                    "到着地「号」",	"到着地施設の種類",	"到着時刻午前・午後・翌午前・翌午後",	"到着時刻時",	"到着時刻分",	"着目的",
                    "交通手段①手段",	"交通手段①所要時間","交通手段①乗換地点","交通手段②手段","交通手段②所要時間","交通手段②乗換地点	",
                    "交通手段③手段",	"交通手段③所要時間","交通手段③乗換地点",	"交通手段④手段","交通手段④所要時間"	,"交通手段④乗換地点",
                    "交通手段⑤手段",	"交通手段⑤所要時間",	"駐輪場所",	"自動車利用運転有無",	"自動車利用自動車の所有者",	"自動車利用乗車人員",
                    "自動車利用駐車場所",	"自動車利用有料道路利用有無",	"自動車利用乗車ICコード",	"自動車利用降車ICコード",	"拡大係数個人",
                    "拡大係数トリップ",	"所有車両自動車台数",	"所有車両二輪車台数",	"所有車両自動車所有の有無",	"所有車両二輪車所有の有無",
                    "トリップ所要時間着時刻－発時刻",	"トリップ所要時間アンリンクト積み上げ",	"発目的",	"目的種類分類0",	"目的種類分類Ⅰ",
                    "目的種類分類Ⅱ",	"目的種類分類Ⅲ","代表交通手段分類0","代表交通手段分類Ⅰ", "代表交通手段分類Ⅱ",	"代表交通手段分類Ⅲ",
                    "マストラ乗車代表交通手段",	"マストラ乗車駅バス停コード",	"マストラ乗車直接端末手段（分類０）",	"マストラ乗車代表端末手段",
                    "マストラ乗車直接端末所要時間",	"マストラ乗車代表端末所要時間",	"マストラ乗車端末全体所要時間",	"マストラ降車代表交通手段",
                    "マストラ降車駅バス停コード",	"マストラ降車直接端末手段",	"マストラ降車代表端末手段",	"マストラ降車直接端末所要時間",
                    "マストラ降車代表端末所要時間",	"マストラ降車端末全体所要時間",	"現住所マッチングレベル",	"現住所緯度",	"現住所経度",
                    "通勤・通学先マッチングレベル",	"通勤・通学先緯度",	"通勤・通学先経度",	"出発地マッチングレベル",	"出発地緯度",
                    "出発地経度", "到着地マッチングレベル",	"到着地緯度",	"到着地経度"))


```

Wrangling

Function to transform coords
```{r}

transform_coords_safe <- function(dt, xcol, ycol, crs_from = 4326, crs_to = 2450) {
  
  # Identify complete coordinate rows
  valid <- !is.na(dt[[xcol]]) & !is.na(dt[[ycol]])
  
  # Prepare output matrix filled with NA
  result <- matrix(NA_real_, nrow = nrow(dt), ncol = 2)
  
  if (any(valid)) {
    sf_obj <- st_as_sf(
      dt[valid],
      coords = c(xcol, ycol),
      crs = crs_from,
      remove = FALSE
    )
    
    sf_obj <- st_transform(sf_obj, crs_to)
    result[valid, ] <- st_coordinates(sf_obj)
  }
  
  return(result)
}
```

```{r}
 df_cleaned <- data.table(matrix(nrow = nrow(df_raw), ncol = 0))    
    df_cleaned[,":="(id_person = df_raw$"整理番号小ゾーン"*100000000000 + df_raw$"整理番号世帯SEQ"*1000000 + 
                        df_raw$"個人番号"*10000 + df_raw$"世帯票年齢"*100 + df_raw$"職業",
                      id_person2 = df_raw$"整理番号小ゾーン", 
                      id_person3 = df_raw$"整理番号世帯SEQ", 
                      id_person4 = df_raw$"個人番号",
                      id_household = df_raw$"整理番号小ゾーン"*1000000 + df_raw$"整理番号世帯SEQ"*100 +
                        df_raw$"世帯人数"*10 + df_raw$"調査年次")]
 
  #tripnum
    df_cleaned[,"tripnum":=as.numeric(df_raw$"トリップ番号")]
  
  #starttime
    setnames(df_raw,"出発時刻午前・午後・翌午前","arriveAMPM")
    setnames(df_raw,"出発時刻時","arriveHour")
    setnames(df_raw,"出発時刻分","arriveMin")
    df_time<-df_raw[,.SD,.SDcols=c("arriveHour","arriveMin","arriveAMPM")]
    df_time[arriveHour==99|arriveMin==99|arriveAMPM==9,":="(arriveHour = 9999, arriveMin = 9999)]
    df_time[arriveAMPM==1,arriveHour:=arriveHour] #converting to military time
    df_time[arriveAMPM==2,arriveHour:=arriveHour+12L] #converting to military time
    df_time[arriveAMPM==3,arriveHour:=arriveHour+24L] 
    df_time[arriveAMPM==4,arriveHour:=arriveHour+36L] 
    
    df_time[,"starttime" := arriveHour * 60 + arriveMin]
    df_time[starttime>9999,"starttime":=-9999]
    df_cleaned[,"starttime":= as.numeric(df_time$starttime)][is.na(starttime),"starttime":=-9999]
  
  #Coordinate
    df_cleaned[,"h_x":=as.numeric(df_raw$"現住所経度")]#[is.na(h_x),"h_x":=-9999]
    df_cleaned[,"h_y":=as.numeric(df_raw$"現住所緯度")]#[is.na(h_y),"h_y":=-9999]
    df_cleaned[,"s_x":=as.numeric(df_raw$"出発地経度")]#[is.na(s_x),"s_x":=-9999]
    df_cleaned[,"s_y":=as.numeric(df_raw$"出発地緯度")]#[is.na(s_y),"s_x":=-9999]
    df_cleaned[,"d_x":=as.numeric(df_raw$"到着地経度")]#[is.na(d_x),"d_x":=-9999]
    df_cleaned[,"d_y":=as.numeric(df_raw$"到着地緯度")]#[is.na(d_y),"d_y":=-9999]
    df_cleaned[,"ws_x":=as.numeric(df_raw$"通勤・通学先経度")]
    df_cleaned[,"ws_y":=as.numeric(df_raw$"通勤・通学先緯度")]
    
    # transform coordinates
    coords_h <- transform_coords_safe(df_cleaned[tripnum != 0], "h_x", "h_y")
    coords_s <- transform_coords_safe(df_cleaned[tripnum != 0], "s_x", "s_y")
    coords_d<- transform_coords_safe(df_cleaned[tripnum != 0], "d_x", "d_y")
    # coords_ws<- transform_coords(df_cleaned[tripnum != 0], "ws_x", "ws_y")
    
    df_cleaned[tripnum != 0, `:=`(
      h_x2450 = coords_h[,1],
      h_y2450 = coords_h[,2],
      
      s_x2450 = coords_s[,1],
      s_y2450 = coords_s[,2],
      
      d_x2450 = coords_d[,1],
      d_y2450 = coords_d[,2]
      # ws_x2450 = coords_ws[,1],
      # ws_y2450 = coords_ws[,2],
    )]
    
  
  #bike
    df_cleaned[,"bike_hhOwnership":=df_raw$"所有車両自転車"]
  
  #age
    df_cleaned[,"age":=as.numeric(df_raw$"世帯票年齢")]
  
  # attributes about household info
    df_cleaned[,"numMemInHH":= as.numeric(df_raw$"世帯人数")]
    df_cleaned[,":="("hasMemAgeLess20" = 0, "hasMemAgeLess6" = 0, "hasMemAgeOver65" =0, "hasMemAgeOver75" = 0)]
    df_cleaned[id_household %in% df_cleaned[age<20,id_household], "hasMemAgeLess20":=1]
    df_cleaned[id_household %in% df_cleaned[age<6,id_household], "hasMemAgeLess6":=1] # NOT CONSISTENT WITH THE FOLLOWING DataUnderSchoolAge FILTERING 
    df_cleaned[id_household %in% df_cleaned[age>65,id_household], "hasMemAgeOver65":=1]
    df_cleaned[id_household %in% df_cleaned[age>75,id_household], "hasMemAgeOver75":=1]
  
  #gender
    df_cleaned[,"male":=0L]
    df_cleaned[df_raw$"世帯票性別"==1,"male":=1]
  
  #license
    setnames(df_raw,"保有運転免許①","license")
    df_cleaned[,"license":=0L]
      df_cleaned[df_raw$license==2,"license":=1] #license = 2 means 免許あり in the questionnaire
    df_cleaned[df_raw$license==9,"license":=9]
  
  #caravailability
    df_cleaned[,"car_availability":=0L]
    df_cleaned[df_raw$"自由に使える自動車"==1,"car_availability":=1]
    df_cleaned[df_raw$"自由に使える自動車"==2,"car_availability":=2]
    df_cleaned[df_raw$"自由に使える自動車"==9,"car_availability":=9]
  
  #car household ownership
    df_cleaned[,"car_hhOwnership":=df_raw$"所有車両自動車台数"]
  
  #job
    df_cleaned[,"jobType":=df_raw$"職業"]
    df_cleaned[,"employType":=df_raw$"就業形態"]
  
  #accompanyNecessity
    df_cleaned[,"accompanyNecessity":=df_raw$"外出の際の付き添い"]
  
  #trip mode
    df_cleaned[,"tripmode":=as.numeric(df_raw$"代表交通手段分類Ⅰ")][is.na(tripmode),"tripmode":=99] #tripmode
    df_cleaned[,"drivingOrNot":=as.numeric(df_raw$"自動車利用運転有無")][is.na(drivingOrNot),"drivingOrNot":=99]  #drivingOrNot
    df_cleaned[,"whoOwnsTheCar":=as.numeric(df_raw$"自動車利用自動車の所有者")]   #who Owns The Car
    df_cleaned[,"carOccupancy":=as.numeric(df_raw$"自動車利用乗車人員")]   #car Occupancy
    df_cleaned[,"usingTollOrNot":=as.numeric(df_raw$"自動車利用有料道路利用有無")]   #using Toll Or Not
    df_cleaned[,"carParkingType":=as.numeric(df_raw$"自動車利用駐車場所")]   # car parking type
    df_cleaned[,"bicParkingType":=as.numeric(df_raw$"駐輪場所")]   # bicycle parking type
  
  
  #trippurpose: purpose at destination
    df_cleaned[,"tripurpose":=as.numeric(df_raw$"着目的")][is.na(tripurpose),"tripurpose":=99]
    df_cleaned[,"depFacilityType" := df_raw$"出発地施設の種類"]
    df_cleaned[,"arrFacilityType" := df_raw$"到着地施設の種類"]
  
  #tripduration
    setnames(df_raw,"トリップ所要時間着時刻－発時刻","tripduration")
    df_cleaned[,"tripduration":=as.numeric(df_raw$tripduration)][is.na(tripduration),"tripduration":=9999]
    df_cleaned[,"arrivetime":=as.numeric(starttime)+as.numeric(tripduration)]
  
  #job aggregate
    df_cleaned[jobType == 1, jobTypeAggr := "prim sector"]
    df_cleaned[jobType %in% c(2,3,4), jobTypeAggr := "seco sector"]
    df_cleaned[jobType %in% c(5,6,7,8,9,10,11,12,13,14,15,16,17,18), jobTypeAggr := "teri sector"]
    df_cleaned[jobType == 19, jobTypeAggr := "other"]
    df_cleaned[jobType %in% c(20,21,22), jobTypeAggr := "student"]
    df_cleaned[jobType %in% c(23,24,25), jobTypeAggr := "unemployed"]
  
  # if you are the 世帯主, then we assume that 自由に使える自動車= 1
    df_cleaned[id_person4 == 1 & car_availability==9 & car_hhOwnership > 0 & car_hhOwnership != 999, car_availability:=1]
  
  # aggregate tripurposes 
    df_cleaned[(tripurpose==1|tripurpose>9) & tripurpose!=99, tripurpose:=1] # including作業as work
    df_cleaned[tripurpose==1&arrivetime<=420, tripurpose:=15]
    df_cleaned[tripurpose==1&arrivetime<=480, tripurpose:=16]
    df_cleaned[tripurpose==1&arrivetime<=540, tripurpose:=17]
    df_cleaned[tripurpose==1&arrivetime<=600, tripurpose:=18]
    df_cleaned[tripurpose==1, tripurpose:=19]
    
    #df_cleaned[tripurpose==8, tripurpose:=2]
    df_cleaned[tripurpose==2&arrivetime<=420, tripurpose:=20]
    df_cleaned[tripurpose==2&arrivetime<=480, tripurpose:=21]
    df_cleaned[tripurpose==2&arrivetime<=540, tripurpose:=22]
    df_cleaned[tripurpose==2&arrivetime<=600, tripurpose:=23]
    df_cleaned[tripurpose==2, tripurpose:=24]
    
    df_cleaned[tripurpose %in% c(15,16,17,18,19), "tripurposeAggr":="work"]
    df_cleaned[tripurpose %in% c(20,21,22,23,24), "tripurposeAggr":="education"]
    df_cleaned[tripurpose==3, "tripurposeAggr":="tohome"]
    df_cleaned[tripurpose==4, "tripurposeAggr":="shopping"]
    df_cleaned[tripurpose %in% c(5,6), "tripurposeAggr":="leisure"]
    df_cleaned[tripurpose==7, "tripurposeAggr":="medical"]
    df_cleaned[tripurpose==8, "tripurposeAggr":="other"]
    df_cleaned[tripurpose==9, "tripurposeAggr":="pickup"]
  
  # aggregate tripmodes
    df_cleaned[tripmode %in% c(1,2,3,4), "CHOICE_mode":="pt"]
    df_cleaned[tripmode %in% c(14,15), "CHOICE_mode":="walk"]
    df_cleaned[tripmode==13, "CHOICE_mode":="bicycle"]
    df_cleaned[tripmode %in% c(6,8,9,10), "CHOICE_mode":="car"]
  # if you are not using car, then these attributes have no meaning
    df_cleaned[CHOICE_mode != "car",":="(drivingOrNot = 99, whoOwnsTheCar = 99, carOccupancy = 99, usingTollOrNot = 99)]
  # if you are using car while has no license, then you must be a passenger
    df_cleaned[CHOICE_mode == "car" & drivingOrNot==9 & license==0, drivingOrNot := 2]
    df_cleaned[CHOICE_mode == "car" & drivingOrNot==1, "CHOICE_mode":="car_driver"]
    df_cleaned[CHOICE_mode == "car" & drivingOrNot==2, "CHOICE_mode":="car_passen"]
    
    
  # number of trips, by person
    df_cleaned[,numOfTrips := max(tripnum), by=id_person]
  
```

Filtering 
```{r}
df_filtered <- df_cleaned


# Missing Values
      df_filtered<-df_filtered[!id_person %in% df_filtered[license==9 | car_availability==9, id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[car_hhOwnership==999, id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[is.na(h_x) | is.na(h_y), id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[jobType == 99, id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[employType == 9, id_person]]
      
  # for has trip only  
      #remove missing values for trip specific variables (only with those had trips)
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & starttime == -9999, id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & tripmode == 99, id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & (tripduration==99 | tripurpose==99) , id_person]]
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & (is.na(s_x) | is.na(s_y) | is.na(d_x) | is.na(d_y)), id_person]]
      
      
# Inexplicable    
      
      # O=D
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & s_x == d_x & s_y == d_y, id_person]]
      
      # remove persons who has "tohome" trips but are not heading home
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & (d_x != h_x | d_y != h_y) & tripurposeAggr == "tohome", id_person]]
  
      # remove first or the last trips that not start/end at home
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum == 1 & (s_x != h_x | s_y != h_y), id_person]] #21382
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & tripnum == numOfTrips & (d_x != h_x | d_y != h_y), id_person]]
    
# Assumption
    # not applicable modes
      df_filtered<-df_filtered[!id_person %in% df_filtered[tripnum != 0 & tripmode %in% c(5,7,11,12,16), id_person]] 
      
      
```

# Prepare for MATSim

Detach plyr, so I can use my normal tidyverse workflow
```{r}
detach("package:plyr", unload = TRUE)
library(tidyverse)
library(tmap)
library(tmaptools)

```



Read municipalities, and aggregate to district level, and translate to english
```{r}
district_dict <- data.frame(
  district_jp = c(
    "前橋市", "高崎市", "桐生市", "伊勢崎市", "太田市",
    "沼田市", "館林市", "渋川市", "藤岡市", "富岡市",
    "安中市", "みどり市", "北群馬郡", "多野郡", "甘楽郡",
    "吾妻郡", "利根郡", "佐波郡", "邑楽郡"
  ),
  district_en = c(
    "Maebashi City", "Takasaki City", "Kiryu City", "Isesaki City", "Ota City",
    "Numata City", "Tatebayashi City", "Shibukawa City", "Fujioka City", "Tomioka City",
    "Annaka City", "Midori City", "Kitagunma District", "Tano District", "Kanra District",
    "Agatsuma District", "Tone District", "Sawa District", "Ora District"
  ),
  stringsAsFactors = FALSE
)

gunma_shp <- st_read("../shared-svn/projects/matsim-gunma/data/raw/01_shapefiles/jis_zones/N03-20_200101.shp",options = "ENCODING=CP932")  %>% mutate(district_jp = case_when(is.na(N03_003)~ N03_004, .default = N03_003)) %>% left_join(district_dict) %>% st_transform(2450) 

gunma_shp_landuse <- gunma_shp %>%
  separate_wider_delim(district_en, delim = " ", names = c(NA,"landuse"), cols_remove = FALSE) %>% 
  st_as_sf()  

   
```


## Output 1: Persons
idx
region_type
gender
employment
age
carAvail = defined as holds license AND has car_availability (exclusive or shared). unknowns are recorded as no 
```{r}

# trips_raw %>% view()
persons <- df_filtered %>% 
  mutate(carAvail = (license == 1 & car_availability %in% c(1,2))) %>% 
  group_by(id_person) %>% 
  summarise(gender = case_when(first(male) == 1 ~ "m", .default = "f"), 
            age = first(age), 
            mobile_on_day = first(numOfTrips) > 0,
            h_x = first(h_x),
            h_y = first(h_y),
            jobTypeAggr = first(jobTypeAggr),
            carAvail = first(carAvail)) %>% 
  st_as_sf(coords = c("h_x","h_y"), crs=4326) %>% 
  st_transform(2450) %>% 
  st_join(gunma_shp_landuse %>% select(landuse)) %>%
  rename(idx = id_person) %>% 
    # the only options are district and city atm
  rename(region_type = landuse) %>% 
  mutate(employment = case_when(jobTypeAggr %in% c("prim sector","seco sector","teri sector") ~ "employed",
                                .default = jobTypeAggr)) %>% 
  select(!jobTypeAggr)

persons %>% st_drop_geometry() %>% 
  write_csv("../shared-svn/projects/matsim-gunma/data/processed/travel_survey/person_attributes.csv")
  
  
  # tmap_mode("view")
  # tm_basemap("Esri.WorldGrayCanvas") + 
  # tm_shape(gunma_shp_landuse %>% st_as_sf()) +
  #   tm_polygons(fill = "landuse") +
  #   tm_shape(persons %>% st_as_sf()) +
  #   tm_dots(alpha = 0.3, size = .1)
  
```


## Output 2: Activities

All agents in this cleaned dataset start their day at home... 
```{r}
df_filtered %>% group_by(id_person) %>% summarise(h_x = first(h_x), h_y = first(h_y),s_x = first(s_x), s_y = first(s_y), numOfTrips = first(numOfTrips)) %>% 
  mutate(chk = ((h_x == s_x) & (h_y == s_y)) | numOfTrips == 0) %>% 
  filter(!chk)

```

for the output:
p_id
type
duration (in minutes)
leg_duration
leg_dist
leg_mode (leg to activity)

So, LL removed all public transit trips from the processed travel survey...
Also, LL removed all act types except for "home","work","other", NA
```{r}

# what leg_modes do we have?
df_filtered %>% pull(CHOICE_mode) %>% unique()
df_filtered %>% pull(tripurposeAggr) %>% unique()

# tripurposeAggr has more information (e.g. doesn't aggregate medical into 'other')
home_acts <- df_filtered %>% 
  group_by(p_id =id_person) %>%
  summarise(duration = first(starttime)) %>%
  mutate(act_num = 0, type = "home", leg_dist = -1, leg_duration = -1)

non_home_acts <- df_filtered %>% 
  mutate(leg_dist = round(sqrt((d_x2450 - s_x2450)^2 + (d_y2450-s_y2450)^2))) %>% 
  mutate(dist_to_home = round(sqrt((d_x2450 - h_x2450)^2 + (d_y2450-h_y2450)^2))) %>% 
    mutate(leg_mode = case_when(CHOICE_mode == "car_driver"~ "car", 
                               CHOICE_mode == "car_passen" ~ "ride",
                               CHOICE_mode == "bicycle" ~ "bike",
                               is.na(CHOICE_mode) ~ "walk",
                                .default = CHOICE_mode)) %>% 
  mutate(type = case_when(tripurposeAggr %in% c("other", "medical", "shopping", "pickup", NA, "leisure") ~ "other",
                          tripurposeAggr == "tohome" ~ "home",
                          .default = tripurposeAggr)) %>% 
  group_by(id_person) %>% 
  mutate(duration = lead(starttime) - arrivetime, duration =  replace_na(duration, -1)) %>%
  ungroup() %>% 
  
  select(p_id =id_person, act_num = tripnum, type, duration , leg_duration = tripduration, leg_mode ,leg_dist,dist_to_home)


combined_acts <- bind_rows(non_home_acts,home_acts) %>% arrange(p_id,act_num)

combined_acts %>% view()
    
write_csv(combined_acts,"../shared-svn/projects/matsim-gunma/data/processed/travel_survey/activities.csv")
```

# Reference Files for SimWrapper

We are going to make the reference files based on our **processed** trips files: 
```{r}

trips_processed <- df_filtered %>% 
  mutate(dist = round(sqrt((d_x2450 - s_x2450)^2 + (d_y2450-s_y2450)^2))) %>% 
  drop_na(dist) %>% 
    mutate(mode = case_when(CHOICE_mode == "car_driver"~ "car", 
                               CHOICE_mode == "car_passen" ~ "ride",
                               CHOICE_mode == "bicycle" ~ "bike",
                               is.na(CHOICE_mode) ~ "walk",
                                .default = CHOICE_mode)) %>% 
  mutate(dist_group = case_when(
    dist < 1000 ~ "0 - 1000",
    dist < 2000 ~ "1000 - 2000",
    dist < 5000 ~ "2000 - 5000",
    dist < 10000 ~ "5000 - 10000",
    dist < 20000 ~ "10000 - 20000",
    .default = "20000+")) %>% 
  filter(mode != "pt") %>% 
  mutate(sex = case_when(male == 0 ~ "Female", .default = "Male")) %>% 
    select(id_person, mode, dist, dist_group, age, sex)


# MODE SHARE (trip based)
trips_processed  %>% 
  group_by(mode) %>% 
  summarise(n = n()) %>% 
  mutate(share = n/sum(n))




```
### Modal Split by Distance class
```{r}


# TRIP BASED MODAL SPLIT, grouped into mode and sit group. 
# sum of share column = 1 
# resources/mode_share_ref.csv
trips_processed %>%
  group_by(mode,dist_group) %>% 
  summarise(n = n(), dist = sum(dist, na.rm = TRUE)) %>% 
  filter(!is.na(mode)) %>%
  ungroup() %>%
  mutate(share_trips = n/sum(n), share_dist = dist/sum(dist)) %>% 
  select(dist_group, main_mode = mode, share = share_trips, share_dist) %>% 
  arrange(dist_group) %>% 
  write_csv("resources/mode_share_ref.csv")

# TRIP BASED MODAL SPLIT, again grouped into mode and dist_group. However, this time the mode shares in each distance group add up to 1.0. This is used for the simwrapper plot row 2 - right. 
# resources/mode_share_per_dist_ref.csv
trips_processed %>%
  group_by(mode,dist_group) %>%
  count() %>% 
  group_by(dist_group) %>% 
  mutate(share = n / sum(n)) %>% 
  arrange(dist_group) %>% 
  select(dist_group, main_mode = mode, share) %>%
  write_csv("resources/mode_share_per_dist_ref.csv")
 
# Share of users that use mode at least once a day:
# "resources/mode_users_ref.csv"
pop_size <- df_filtered  %>% pull(id_person) %>% unique() %>% length()


trips_processed %>% glimpse()
trips_processed  %>% 
  group_by(id_person,mode) %>% 
  summarise(uses_mode = TRUE) %>% 
  pivot_wider(names_from = mode, values_from = uses_mode, values_fill = FALSE) %>% 
  pivot_longer(-id_person, names_to = "mode",values_to = "uses_mode") %>%
  group_by(mode) %>% 
  summarise(n = sum(uses_mode)) %>% 
  mutate(share = n / pop_size) %>% 
  filter(mode != "NA") %>% 
  select(main_mode = mode, user = share) %>%
  write_csv("resources/mode_users_ref.csv")


# resources/mode_share_distance_distribution.csv
# takes share only of mobile people
trips_processed %>% 
  mutate(dist_rounded = round(dist,-2)) %>%
  group_by(mode, dist_rounded) %>%
  count() %>% 
  group_by(dist_rounded) %>% 
  mutate(share = n/sum(n)) %>% 
  select(mode, share) %>% 
  ungroup() %>% pivot_wider(names_from = mode,values_from = share, values_fill = 0.0) %>% 
  rename(dist = dist_rounded) %>% arrange(dist) %>%
  filter(dist <=30000) %>% 
  write_csv("resources/mode_share_distance_distribution.csv")
  


```

# Explaratory Analysis

### Modal Split by Age
```{r}
trips_processed %>% 
  mutate(ageGr = case_when(
    age >= 85 ~ "85+",
    age >= 75 ~ "75-84",
    age >= 65 ~ "65-74",
    age >= 18 ~ "18-64",
    .default = "0-17"
    )
  ) %>% 
  select(ageGr,mode, dist) %>%
  group_by(ageGr, mode) %>% 
  summarise(n = n(), dist = sum(dist, na.rm = TRUE)) %>%
  group_by(ageGr) %>%
  mutate(share_trips = n/sum(n), share_dist = dist/sum(dist)) %>% 
  ggplot() +
  geom_col(aes(ageGr,share_trips,fill = mode)) +
  theme_minimal(base_size = 14)


```

On my filtered population:
```{r}


persons %>% st_drop_geometry() %>%  filter(age >=95) %>% group_by(gender,region_type) %>% count()
```



### License

License:
- 0 = no
- 1 = yes
- 9 = unknown

car_availability
- 0 = no
- 1 = yes, exclusive
- 2 = yes, shared
- 9 = unknown
```{r}
# license only
df_filtered %>%
  select(id_person,age, male,license, car_availability) %>%
  group_by(id_person) %>% 
  summarise(age = first(age), male = first(male), license = first(license), car_availability = first(car_availability)) %>% 
    mutate(carAvail = (license == 1)) %>% 
  # filter(license!=9) %>% 
  mutate(age_group = case_when(age >= 85 ~ "85+", age >= 75 ~ "75-84", age >= 65 ~ "65-74", age >= 18 ~ "18-64", .default = "0-17" )) %>% 
  group_by(age_group, male) %>% 
  summarise(carAvail = sum(carAvail) / n()) %>% mutate(gender = factor(male, levels = c(0,1), labels = c("female","male") )) %>% 
  ggplot() + geom_col(aes(age_group,carAvail, fill = gender), position = "dodge")


# License & CarAvail 
df_filtered %>%
  select(id_person,age, male,license, car_availability) %>%
  group_by(id_person) %>% 
  summarise(age = first(age), male = first(male), license = first(license), car_availability = first(car_availability)) %>% 
  mutate(carAvail = (license == 1 & car_availability %in% c(1,2))) %>% 
  mutate(age_group = case_when(age >= 85 ~ "85+", age >= 75 ~ "75-84", age >= 65 ~ "65-74", age >= 18 ~ "18-64", .default = "0-17" )) %>% 
  group_by(age_group, male) %>% 
  summarise(carAvail = sum(carAvail) / n()) %>% mutate(gender = factor(male, levels = c(0,1), labels = c("female","male") )) %>% 
  ggplot() + geom_col(aes(age_group,carAvail, fill = gender), position = "dodge")

```

