---
title: "process_traffic_counts"
output: html_document
date: "2026-02-11"
---

# Frontmatter

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries
```{r}
library(tidyverse)
library(sf)
library(purrr)
library(stringr)
library(tmap)
library(units)
```

## Functions
```{r}

match_traffic_to_osm <- function(
  traffic_sf,
  osm_sf,
  traffic_id_col = "shortNo",
  osm_id_col     = "osm_id",
  buffer_dist    = 10,          # meters
  min_overlap_m  = 20,           # minimum overlap length
  max_angle_diff = 45, 
  return_sf      = FALSE        # return geometries or plain table
) {
  
  
  # -----------------------------
  # 1. Check CRS
  # -----------------------------
  if (st_crs(traffic_sf) != st_crs(osm_sf)) {
    stop("CRS of traffic_sf and osm_sf must be identical.")
  }
  
  if (is.na(st_crs(traffic_sf)$units_gdal) ||
      st_crs(traffic_sf)$units_gdal != "metre") {
    stop("CRS must be projected in meters (e.g. EPSG:2450).")
  }
  
  
  # -----------------------------
  # 2. Add bearings
  # -----------------------------
  traffic_sf$traffic_bearing_deg <- sapply(st_geometry(traffic_sf), compute_bearing)
  osm_sf$osm_bearing_deg         <- sapply(st_geometry(osm_sf), compute_bearing)
  
  
  # -----------------------------
  # 2. Buffer traffic lines
  # -----------------------------
  traffic_buf <- st_buffer(traffic_sf, buffer_dist)
  
  # Keep only ID + geometry to speed up intersection
  traffic_buf <- traffic_buf %>%
    select(!!traffic_id_col,traffic_bearing_deg)
  
  osm_small <- osm_sf %>% mutate(osm_length =  as.numeric(st_length(.))) %>% 
    select(!!osm_id_col,osm_length,osm_bearing_deg)
  
  
  
  # -----------------------------
  # 3. Compute intersections
  # -----------------------------
  # resulting geometry contains part of MATSim link that is within buffer of MLIT link
  overlaps <- st_intersection(
    traffic_buf,
    osm_small
  )
  
  if (nrow(overlaps) == 0) {
    warning("No overlaps found.")
    return(NULL)
  }
  

  # -----------------------------
  # 4. Calculate overlap length
  # -----------------------------
  overlaps$overlap_length_m <- as.numeric(st_length(overlaps))
  
  # overlaps <- overlaps %>%
  #   filter(overlap_length_m >= min_overlap_m)
  
  if (nrow(overlaps) == 0) {
    warning("No overlaps above min_overlap_m.")
    return(NULL)
  }
  
  
  
# overlaps %>%
#   st_collection_extract("LINESTRING") %>%
#   st_cast("LINESTRING") %>%     st_line_sample(n = 10)



  traffic_part <- st_intersection(
    traffic_sf,
    st_buffer(osm_sf, buffer_dist)
  )

  overlaps$mean_dist_m <- mapply(
    mean_line_distance,
    st_geometry(traffic_part),
    st_geometry(osm_sf[match(overlaps[[osm_id_col]], osm_sf[[osm_id_col]]), ])
  )
  # -----------------------------
  # 5. Compute length shares
  # -----------------------------
  overlaps <- overlaps %>%
    group_by(.data[[traffic_id_col]]) %>%
    mutate(
      overlap_share = overlap_length_m / sum(overlap_length_m)
    ) %>%
    ungroup()
  
    # -----------------------------
  # 6. Direction comparison
  # -----------------------------
  overlaps <- overlaps %>%
    mutate(
      angle_diff_deg = abs(traffic_bearing_deg - osm_bearing_deg),
      angle_diff_deg = ifelse(angle_diff_deg > 180,
                              360 - angle_diff_deg,
                              angle_diff_deg),
      direction_relation = case_when(
        angle_diff_deg <= max_angle_diff ~ "same",
        abs(angle_diff_deg - 180) <= max_angle_diff ~ "opposite",
        TRUE ~ "other"
    )
    )
  
  
  # -----------------------------
  # 5.5. Share of OSM Link that is in Buffer
  # -----------------------------
  overlaps <- overlaps %>% mutate(share_of_osm_link_in_buffer = overlap_length_m/osm_length)
  
  # -----------------------------
  # 6. Return result
  # -----------------------------
  if (!return_sf) {
    overlaps <- overlaps %>%
      st_drop_geometry()
  }
  
  return(overlaps)
}


compute_bearing <- function(geom) {
  coords <- st_coordinates(geom)
  
  start <- coords[1, 1:2]
  end   <- coords[nrow(coords), 1:2]
  
  dx <- end[1] - start[1]
  dy <- end[2] - start[2]
  
  angle <- atan2(dx, dy) * 180 / pi
  if (angle < 0) angle <- angle + 360
  
  return(angle)
}



mean_line_distance <- function(line_a, line_b, step = 5) {

  clean <- function(g) {
    g <- st_collection_extract(g, "LINESTRING") %>% st_cast("LINESTRING")
    if (length(g) == 0) return(NULL)
    st_union(g)
  }

  line_a <- clean(line_a)
  line_b <- clean(line_b)

  if (is.null(line_a) || is.null(line_b)) return(NA_real_)

  dense <- st_segmentize(line_a, dfMaxLength = step)
  pts <- st_cast(dense, "POINT")

  d <- as.numeric(st_distance(pts, line_b))
  mean(d)
}
```

# ---- Find files ----
```{r}

input_dir <- "/Users/jakob/scrape_mlit2/clean"
target_crs <- 2450

files <- list.files(
  input_dir,
  pattern = "\\.geojson$",
  full.names = TRUE
)

if (length(files) == 0) {
  stop("No GeoJSON files found.")
}

cat("Found", length(files), "files\n")
```

# ---- Read + merge safely ----

```{r}
gdfs <- map(files, function(f) {
  tryCatch({
    # cat("Reading", basename(f), "\n")

    gdf <- st_read(f, quiet = TRUE) %>% st_transform(target_crs)

    # Extract numeric ID from filename (0003.geojson -> 3)
    file_id <- str_extract(basename(f), "\\d+") |> as.integer()

    gdf$file_id <- file_id

    gdf
  }, error = function(e) {
    message("Skipping ", basename(f), ": ", e$message)
    NULL
  })
})

# Remove failed reads
gdfs <- compact(gdfs)

if (length(gdfs) == 0) {
  stop("No valid GeoJSON files could be read.")
}


```
# ---- Merge ----

```{r}

merged <- bind_rows(gdfs)

cat("Merged", nrow(merged), "features\n")
```

# Read Kasyo file, to create a key between shortNo and longNo

Key: Basic Traffic Survey Section Number -> Survey Unit Section Number
Left is used by geojson. Right is used in the hourly traffic volume spreadsheet. 
```{r}
roads_counts_kasyo <- read_csv("../shared-svn/projects/matsim-gunma/data/raw/road_counts/mlit/kasyo10.csv", locale = locale(encoding = "CP932")) 

roads_counts_kasyo_key <- roads_counts_kasyo %>% select(longNo = "交通調査基本区間番号...1", shortNo = "交通量／調査単位区間番号", longNoOfStationUpbound = "上り／観測地点交通調査基本区間番号", longNoOfStationDownbound = "下り／観測地点交通調査基本区間番号", longNoOfConnectingRoadStart = "起点側／交通調査基本区間番号", longNoOfConnectingRoadEnd = "終点側／交通調査基本区間番号" )


# upward station and downward station are always the same :)
roads_counts_kasyo_key %>% filter(longNoOfStationUpbound!=longNoOfStationDownbound)


# only looking the actual counting facilities, we only have 857 measuring stations (instead of 2107). However, we will have upward and downward eventually. 4 of these stations are not acutally in our file. So they disappear in the next step.
roads_counts_kasyo_key$longNoOfStationUpbound %>% unique() %>% length()


# there are 853 unique shortNo - longNo combos
roads_counts_kasyo_key_condensed <- roads_counts_kasyo_key %>% filter(longNo == longNoOfStationUpbound)
roads_counts_kasyo_key_condensed %>% pull(longNo) %>% unique() %>% length()
roads_counts_kasyo_key_condensed %>% pull(shortNo) %>% unique() %>% length()


```

SHAPE FILE 
```{r}

tmap_mode("view")

tm_shape(merged)+tm_lines()

# st_write(merged, output_gpkg, delete_dsn = TRUE)
# st_write(merged, output_geojson, delete_dsn = TRUE)

cat("Done.\n")



road_counts_shp <- merged %>% 
  separate_wider_position(census,widths = c("Prefecture" = 2,"Unknown1" = 1,"Route" = 5,"Unkown2" = 3),cols_remove = FALSE) %>%
  filter(Prefecture == "10") %>% 
  mutate(longNo = as.numeric(census))%>% 
  inner_join(roads_counts_kasyo_key_condensed, by = c("longNo")) %>% st_as_sf() %>% group_by(shortNo) %>% summarise()


tm_shape(road_counts_shp) +
  tm_lines(col = "shortNo")

```


```{r}
road_counts <- read_csv("../shared-svn/projects/matsim-gunma/data/raw/road_counts/mlit/zkntrf10.csv", locale = locale(encoding = "CP932"))

col_dict <- c(
  "都道府県指定市コード" = "prefecture_code",
  "交通量調査単位区間番号" = "traffic_section_id",
  "道路種別" = "road_type",
  "路線番号" = "route_number",
  "令和３年度調査交通量観測・非観測の別" = "observed_flag",
  "個別調査観測値活用の別" = "individual_observation_flag",
  "１２・２４時間観測の別" = "survey_duration_type",
  "交通量観測年月日" = "survey_date",
  "天候" = "weather",
  "上り・下りの別" = "direction",
  "車種区分" = "vehicle_type",
  "昼間１２時間自動車類交通量（台）" = "traffic_12h_total",
  "２４時間自動車類交通量（台）" = "traffic_24h_total"
)

# Full-width Japanese digits → normal digits
jp_hours <- c("０","１","２","３","４","５","６","７","８","９",
              "１０","１１","１２","１３","１４","１５",
              "１６","１７","１８","１９","２０","２１","２２","２３")

for (h in 0:23) {
  jp_h <- jp_hours[h + 1]
  old_name <- paste0("時間帯別自動車類交通量（台／時）／", jp_h, "時台")
  new_name <- paste0("traffic_", sprintf("%02d", h), "h")
  col_dict[old_name] <- new_name
}

names(road_counts) <- col_dict[names(road_counts)]




# col_dict %>% view()


```
### Analyse Ratio Heavy vs. Light traffic:

```{r}
road_counts %>% 
  select(traffic_section_id,direction,vehicle_type,traffic_12h_total) %>%
  filter(!is.na(traffic_12h_total)) %>%
  pivot_wider(names_from = vehicle_type, values_from = traffic_12h_total) %>% 
  summarise(light_vehicle_share = sum(`1`)/sum(`1` + `2`))
```


We now take average of upbound/downbound
1: Upbound
2: Downbound

NOTE: some links are only upbound/downbound.
We only examine small vehicles 
1: Small vehicle
2: Large vehicle
```{r}
# road_counts %>% view()

# ONLY FOR SMALL VEHICLES AND IN ONE DIRECTION!
road_counts_merged <- road_counts %>%
  mutate(shortNo = traffic_section_id) %>%
  filter( vehicle_type == 1) %>% select(shortNo, starts_with("traffic"), -traffic_section_id) %>%
  group_by(shortNo) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE), dirs = n()) %>% 
  inner_join(road_counts_shp, by = "shortNo") %>% st_as_sf()

tm_shape(road_counts_merged) + 
  tm_lines(col = "traffic_12h_total", palette = "viridis")
```

Which roads did not get a shape file?
33 reads. I've checked a few of them, and they seem at the outskirts. So I just gotta do it again.
```{r}

road_counts_merged |>
  filter(sf::st_is_empty(geometry))


# road_counts_merged %>% filter(g)
```


# Read & Process MATSim Network
Read and convert MATSim geometries

 [1] "highway.unclassified"   "highway.residential"    "highway.tertiary"       "highway.cycleway"      
 [5] "highway.secondary"      "highway.trunk"          "highway.primary"        "highway.motorway_link" 
 [9] "highway.trunk_link"     "highway.path"           "highway.secondary_link" "highway.primary_link"  
[13] "highway.service"        "highway.motorway"    
```{r}


# Read the CSV
matsim_network_geos_raw <- read.csv("input/v1.4/gunma-v1.4-network-linkGeometries.csv", stringsAsFactors = FALSE)

# Read MATSim Network, so as to only keep match links that are actually present in the network:
matsim_cleaned_network <- matsim::read_network("input/v1.4/gunma-v1.4-network.xml")

ids_matsim_cleaned_network <- matsim_cleaned_network$links %>% 
  filter(!type %in% c("highway.path","highway.cycleway","highway.residential")) %>%  pull(id)

# filter geometries to only include those

matsim_network_geos <- matsim_network_geos_raw %>% filter(LinkId %in% ids_matsim_cleaned_network)

# Function to convert the Geometry column into a MULTILINESTRING
parse_multilinestring <- function(geom_str) {
  # Split by "),(" to separate points
  coords <- str_extract_all(geom_str, "\\(([^)]+)\\)")[[1]]
  
  # Convert each "(x,y)" into numeric vector
  coords_list <- lapply(coords, function(x) {
    nums <- str_remove_all(x, "[()]") %>% str_split(",") %>% unlist()
    as.numeric(nums)
  })
  
  # In this file, each row seems to be a single line (so just wrap as one line)
  st_multilinestring(list(do.call(rbind, coords_list)))
}

# Apply to each row
matsim_network_geos_sf <- matsim_network_geos %>%
  rowwise() %>%
  mutate(geometry = st_sfc(parse_multilinestring(Geometry))) %>%
  st_as_sf() %>%
  ungroup()

st_crs(matsim_network_geos_sf) <- 2450

saveRDS(matsim_network_geos_sf, "../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf.rds")


gunma <- st_read("/Users/jakob/git/shared-svn/projects/matsim-gunma/data/raw/01_shapefiles/zzz_deprecated/gunma_2450/gunma_2450.shp")
matsim_network_geos_sf_filtered <- matsim_network_geos_sf %>% st_filter(gunma)

saveRDS(matsim_network_geos_sf_filtered, "../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf_filtered.rds")


matsim_network_geos_sf <- readRDS("../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf.rds")
matsim_network_geos_sf_filtered <- readRDS("../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf_filtered.rds")



# 

```


# Matching process
```{r}
# we are only looking at counting stations with all 24 hours: 129 stations
road_counts_merged_filtered <- road_counts_merged %>% 
  drop_na(traffic_24h_total) %>% 
  st_transform(2450)

# Do the actual matching process. 

matsim_to_mlit_merge <-  match_traffic_to_osm(road_counts_merged_filtered,matsim_network_geos_sf_filtered, min_overlap_m = 50,  buffer_dist = 15, osm_id_col = "LinkId")
```

# Final Filtering
For now, we will only examine 24 hour values. And we will try to find 

I need to somehow specify this such that each MATSim link only shows up as a single counting station
```{r}
# This will link to multiple links. Now we have to choose the 
matsim_to_mlit_merge_filtered <- matsim_to_mlit_merge %>% 
  # group_by(shortNo, LinkId) %>% 
  # summarise(mean_dist_m = mean(mean_dist_m), overlap_length_m = sum(overlap_length_m),) %>% 
  filter(direction_relation !="other") %>% 
  filter(overlap_length_m > 100) %>%
  
  
  # filter(direction_relation == "same") %>% view()
  group_by(shortNo) %>% 
  # filter(share_of_osm_link_in_buffer ==  max(share_of_osm_link_in_buffer)) %>% 
  filter(mean_dist_m == min(mean_dist_m)) %>%
  slice_head() 
  # filter(angle_diff_deg == min(angle_diff_deg))
  # mutate(shortNo = str_replace_all(shortNo, "[A-Za-z]*",""))

matsim_to_mlit_merge_filtered %>% pull(LinkId) %>% unique() %>% length()
matsim_to_mlit_merge_filtered %>% pull(shortNo) %>% unique() %>% length()
```

plot
```{r}
matsim_final_filtered <- matsim_network_geos_sf_filtered %>% 
  filter(LinkId %in% (matsim_to_mlit_merge_filtered %>% pull(LinkId) %>% unique())) %>% select(LinkId)

mlit_final_filtered <- road_counts_merged %>% 
  filter(shortNo %in% (matsim_to_mlit_merge_filtered %>%  pull(shortNo) %>% unique())) %>% select(shortNo)


tm_shape(matsim_network_geos_sf_filtered) +
tm_lines(col = "yellow", lwd = 0.2) +
tm_shape(matsim_final_filtered) + 
tm_lines(col = "red", lwd = 3) + 
tm_shape(mlit_final_filtered) +
tm_lines(col = "black", lty = 2 ) 
  # tm_shape(sf::st_endpoint(mlit_final_filtered)) +
  # tm_dots()
```

to csv
```{r}
ready_for_csv <- matsim_to_mlit_merge_filtered %>% 
  select(LinkId, shortNo) %>% 
  # mutate(LinkIdRev = case_when(str_starts(LinkId, "-") ~ str_replace(LinkId, "-",""), .default = paste0("-", LinkId))) %>%
  # pivot_longer(c(LinkId,LinkIdRev), names_to = "cat",values_to = "LinkId") %>% select(-cat) %>% 
  # filter(LinkId %in% ids_matsim_cleaned_network) %>% 
  mutate(shortNo = as.numeric(shortNo)) %>% 
  left_join(road_counts_merged_filtered %>% st_drop_geometry()) %>% 
  pivot_longer(matches("traffic_[0-9]"),names_to = "time",values_to = "count") %>% 
  select(LinkId,shortNo,time,count) %>% filter(!is.na(count)) %>% 
  arrange(shortNo,LinkId,time)
  
# ready_for_csv %>% view()
ready_for_csv %>% pull(LinkId) %>% unique() %>% length()
ready_for_csv %>% pull(shortNo) %>% unique() %>% length()


  write_csv(ready_for_csv,"../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_linkId_to_roadcounts.csv")

```








# DEPRECATED


```{r}


# we duplicate these, so that we have a forward and backwards direction: 258 stations
# we give each station the mean count between the forward and backward direction from
# the MLIT dataset. 
# road_counts_merged_duplicated <- road_counts_merged_filtered %>% 
#   mutate(shortNo = paste0(shortNo,"forward")) %>% 
#   bind_rows(
#     road_counts_merged_filtered %>%
#       mutate(geometry = st_reverse(geometry),
#              shortNo = paste0(shortNo,"backward")))

```


```{r}

testy <- roads_counts_kasyo_key_condensed %>% 
  inner_join(road_counts_shp) %>% st_as_sf() 



get_start <- function(g) {
  coords <- st_coordinates(g)
  st_point(coords[1, c("X", "Y")])
}

get_end <- function(g) {
  coords <- st_coordinates(g)
  st_point(coords[nrow(coords), c("X", "Y")])
}

  

testy$start <- st_sfc(
  lapply(st_geometry(testy), get_start),
  crs = st_crs(testy)
)

testy$end <- st_sfc(
  lapply(st_geometry(testy), get_end),
  crs = st_crs(testy)
)

testy <- testy %>% st_drop_geometry()

testy <- testy %>% left_join(road_counts_shp, by = c("longNoOfStationUpbound" = "shortNo")) %>% st_as_sf()

testy %>% view()

testy$upbound_start <- st_sfc(
  lapply(st_geometry(testy), get_start),
  crs = st_crs(testy)
)

testy$upbound_end <- st_sfc(
  lapply(st_geometry(testy), get_end),
  crs = st_crs(testy)
)

testy <- testy %>% st_drop_geometry() 

# %>% left_join(road_counts_shp, by = c("longNoOfStationDownbound" = "shortNo"))

testy$downbound_start <- st_sfc(
  lapply(st_geometry(testy), get_start),
  crs = st_crs(testy)
)

testy$downbound_end <- st_sfc(
  lapply(st_geometry(testy), get_end),
  crs = st_crs(testy)
)

testy %>% view()
```


```{r}

truncate_road_to_Xm <- function(sf_obj, length_m = 100) {
  
  # total length of each line
  line_length <- as.numeric(st_length(sf_obj))
  
  
  # fraction of total length corresponding to 100m
  frac <- as.numeric(length_m / line_length)
  
  # start and end fractions around midpoint (0.5)
  start_frac <- 0.5 - frac / 2
  end_frac   <- 0.5 + frac / 2
  
  # clamp values to [0,1]
  start_frac <- pmax(0, start_frac)
  end_frac   <- pmin(1, end_frac)
  
  sf_obj$geometry <- st_line_substring(
    sf_obj$geometry,
    from = start_frac,
    to   = end_frac
  )
  
  return(sf_obj)
}
```

And now the money question: can I map these to OSM easily? 

```{r}

# osm_shp <- read_sf("../shared-svn/projects/matsim-gunma/data/processed/gunma.osm.pbf")
# 
# osm_shp %>%  filter(st_geometry_type(geometry) == "LINESTRING")
# library(osmdata)

# gunma_shp <- st_read("../shared-svn/projects/matsim-gunma/data/raw/shp/gunma_municip_2020/N03-20200101_10_GML/N03-20_10_200101.shp")


osm_lines <- st_read("../shared-svn/projects/matsim-gunma/data/processed/gunma.osm.pbf", layer = "lines")
# osm_multilinestrings <- st_read("../shared-svn/projects/matsim-gunma/data/processed/gunma.osm.pbf", layer = "multilinestrings")

osm_lines_filtered <- osm_lines %>%  filter(highway %in% c("motorway","trunk","primary","secondary","tertiary","service","unclassified","track")) #tertiary

# osm_lines %>% filter(!is.na(highway)) %>% tm_shape(osm_lines) + tm_lines()

tm_shape(osm_lines_filtered) + 
  tm_lines(col = "red") + 
  tm_shape(road_counts_merged) + 
  tm_lines(col = "black", lty = 3, lwd = 2)
 


```



```{r}

# lichen_matsim_network <- matsim::read_network("../shared-svn/projects/matsim-gunma/data/raw/matsim_inputs_lichen_luo/NetworkRed191211fromJOSM_noHighway_cle_speed0.66Adjusted.xml")
# 
# lichen_matsim_network_sf <- lichen_matsim_network$links  %>%
#   mutate(
#     geometry = pmap(
#       list(x.from, y.from, x.to, y.to),
#       ~ st_linestring(matrix(c(..1, ..2,
#                                ..3, ..4),
#                              ncol = 2,
#                              byrow = TRUE))
#     )
#   ) %>%
#   st_as_sf(crs = 2450)


osm_to_mlit_merge <-  match_traffic_to_osm(road_counts_merged %>% st_transform(2450),osm_lines_filtered %>% st_transform(2450), min_overlap_m = 50,  buffer_dist    = 15) 

osm_to_mlit_merge_filtered <- osm_to_mlit_merge %>% group_by(shortNo) %>% filter(overlap_share == max(overlap_share))


# yyyy2 <- yyyy %>% filter(share_of_osm_link_in_buffer > 0.2)
# tm_shape(osm_lines_filtered %>% select(osm_id,highway)) + 
  # tm_lines(col = "green") + 
# tm_shape(lichen_matsim_network_sf) +
# tm_lines(col = "green") +
tm_shape(osm_lines_filtered %>% filter(osm_id %in% (osm_to_mlit_merge_filtered %>% pull(osm_id) %>% unique())) %>% select(osm_id)) + 
  tm_lines(col = "red") + 
  tm_shape(road_counts_merged %>% filter(shortNo %in% (osm_to_mlit_merge_filtered %>% pull(shortNo) %>% unique())) %>% select(shortNo)) + 
  tm_lines(col = "black", lty = 3 )


tm_shape(osm_lines %>% filter(!is.na(highway) & highway != "footway") %>% select(osm_id, highway)) +
  tm_lines(col = "green") +
# tm_shape(osm_lines_filtered %>% filter(osm_id %in% (!yyyy %>% pull(osm_id) %>% unique())) %>% select(osm_id)) + 
#   tm_lines(col = "red") + 
  tm_shape(road_counts_merged %>% filter(!shortNo %in% (yyyy %>% pull(shortNo) %>% unique())) %>% select(shortNo)) + 
  tm_lines(col = "black", lwd = 5)
```


```{r}
xxxx <- match_lines_by_overlap(road_counts_merged %>% st_transform(2450),osm_lines_filtered %>% st_transform(2450))

tm_shape(osm_lines_filtered %>% filter(osm_id %in% (xxxx %>% pull(".osm_id") %>% unique()))) + 
  tm_lines(col = "red") + 
  tm_shape(road_counts_merged %>% filter(shortNo %in% (xxxx %>% pull(".traffic_id") %>% unique()))) + 
  tm_lines(col = "black", lty = 3 )

tm_shape(osm_lines_filtered) + 
  tm_lines(col = "red") + 
  tm_shape(road_counts_merged %>% filter(! shortNo %in% (xxxx %>% pull(".traffic_id") %>% unique()))) + 
  tm_lines(col = "black", lty = 3, lwd = 2)
```



```{r}
match_lines_by_overlap <- function(
  traffic,
  osm,
  buffer = 15,              # meters
  min_overlap_ratio = 0.3,  # require at least this fraction of traffic segment overlapping
  max_distance = NULL       # optional distance filter in meters
) {
  
  # --- Ensure projected CRS ---
  if (st_is_longlat(traffic)) {
    stop("Traffic data must be in projected CRS (meters).")
  }
  if (st_is_longlat(osm)) {
    stop("OSM data must be in projected CRS (meters).")
  }
  
  # --- Add IDs ---
  traffic <- traffic %>%
    mutate(.traffic_id = shortNo)
  
  osm <- osm %>%
    mutate(.osm_id = osm_id)
  
  # --- Optional distance pre-filter (speeds things up) ---
  if (!is.null(max_distance)) {
    idx <- st_is_within_distance(traffic, osm, dist = max_distance)
    candidate_pairs <- tibble(
      .traffic_id = rep(seq_len(nrow(traffic)), lengths(idx)),
      .osm_id = unlist(idx)
    )
    
    traffic <- traffic %>% filter(.traffic_id %in% candidate_pairs$.traffic_id)
    osm <- osm %>% filter(.osm_id %in% candidate_pairs$.osm_id)
  }
  
  # --- Buffer OSM ---
  osm_buffered <- st_buffer(osm, dist = buffer)
  
  # --- Intersect ---
  intersections <- st_intersection(
    traffic,
    osm_buffered
  )
  
  if (nrow(intersections) == 0) {
    warning("No overlaps found.")
    return(NULL)
  }
  
  # --- Compute overlap length ---
  intersections <- intersections %>%
    mutate(
      overlap_length = as.numeric(st_length(geometry))
    )
  
  # --- Add original traffic length ---
  traffic_lengths <- traffic %>%
    mutate(traffic_length = as.numeric(st_length(geometry))) %>%
    st_drop_geometry()
  
  intersections <- intersections %>%
    left_join(traffic_lengths, by = ".traffic_id") %>%
    mutate(
      overlap_ratio = overlap_length / traffic_length
    )
  
  # --- Select best match per traffic segment ---
  best_matches <- intersections %>%
    group_by(.traffic_id) %>%
    slice_max(overlap_length, n = 1, with_ties = FALSE) %>%
    ungroup()
  
  # --- Apply overlap threshold ---
  best_matches <- best_matches %>%
    filter(overlap_ratio >= min_overlap_ratio)
  
  # --- Return clean lookup ---
  lookup <- best_matches %>%
    st_drop_geometry() %>%
    select(.traffic_id, .osm_id, overlap_length, overlap_ratio)
  
  return(lookup)
}
```
