---
title: "process_road_counts2"
output: html_document
---

# Front Matter

```{r}
library(tidyverse)
library(tmap)
library(sf)
library(lubridate)
library(matsim)
```

# Process Single Data Sources
## JARTIC
Produces jartic_stations_filtered


read geometries (lines and points) 
```{r}
geo_lines <- st_read(
  "../shared-svn/projects/matsim-gunma/data/raw/road_counts/jartic/locations/断面交通量データ＿群馬/Shp/300F_群馬_矢印.shp",
  options = "ENCODING=CP932"
  )  %>% rename(
    station_id = `地点番号`,
    station_name = `地点名称`,
    mesh_code = `メッシュ`,
    link_type = `リンク区分`,
    link_id = `リンク番号`,
    version = `バージョン`,
    geometry = geometry
  ) %>% st_transform(2450)

geo_lines_end <- st_line_sample(geo_lines, sample = 1, type = "regular") %>% st_cast("POINT")

geo_points <- st_read(
  "../shared-svn/projects/matsim-gunma/data/raw/road_counts/jartic/locations/断面交通量データ＿群馬/Shp/300F_群馬_計測地点.shp",
  options = "ENCODING=CP932"
  )%>%
  rename(
    station_id = `地点番号`,
    station_name = `地点名称`,
    mesh_code = `メッシュ`,
    link_type = `リンク区分`,
    link_id = `リンク番号`,
    version = `バージョン`
  ) %>% st_transform(2450) 

colnames(geo_points)

# tmap_mode("view")
# tm_shape(geo_lines) + tm_lines() + 
#   tm_shape(geo_lines_end) + tm_dots(group = "line_end")  
  # tm_shape(geo_points) + tm_symbols(fill = "blue",group = "center")


# geo_lines %>% view()
```


read and rename counts data
```{r}
jartic_data <- read_csv(
  "../shared-svn/projects/matsim-gunma/data/raw/road_counts/jartic/counts/2026_01/typeB_gumma_2026_01/群馬県警_202601.csv",
  locale = locale(encoding = "CP932")
) %>% 
    rename(
    time = `時刻`,
    source_code = `情報源コード`,
    station_id = `計測地点番号`,
    station_name = `計測地点名称`,
    mesh2_code = `2次メッシュコード`,
    link_type = `リンク区分`,
    link_id = `リンク番号`,
    traffic_volume = `断面交通量`,
    distance_from_link_end_10m = `リンク終端からの距離（×10m）`,
    link_version = `リンクバージョン`
  )


```

Filter
723 stations have records on 2026-01-15
723 station have at least 1 hour that has 12 entries (5 minute intervals.)
474 stations have 24 hours with 12 entries (full data set)


```{r}
jartic_data_filtered1 <- jartic_data %>% 
  separate_wider_delim(time, delim = " ", names = c("date","time")) %>% 
  filter(date == "2026/01/15") %>% 
  select(station_id,time, traffic_volume)  %>% 
  mutate(time = hm(time)) %>% 
  mutate(hour = hour(time), minute = minute(time)) %>%
 group_by(station_id,hour) %>% 
  summarise(hourly_volume = sum(traffic_volume), cnt = n())  %>% filter(cnt ==12) %>% view()

jartic_stations_filtered <- jartic_data_filtered1 %>% group_by(station_id) %>% count() %>% filter(n == 24) %>% pull(station_id) %>% unique()

jartic_data_filtered2 <- jartic_data_filtered1 %>% filter(station_id %in% jartic_stations_filtered)

```
## MLIT

### Shape Files

Find geojsons
```{r}

input_dir <- "../shared-svn/projects/matsim-gunma/data/raw/road_counts/mlit/scrape_mlit2/clean/"
target_crs <- 2450

files <- list.files(
  input_dir,
  pattern = "\\.geojson$",
  full.names = TRUE
)

if (length(files) == 0) {
  stop("No GeoJSON files found.")
}

cat("Found", length(files), "files\n")
```

Read geojsons

```{r}
gdfs <- map(files, function(f) {
  tryCatch({
    # cat("Reading", basename(f), "\n")

    gdf <- st_read(f, quiet = TRUE) %>% st_transform(target_crs)

    # Extract numeric ID from filename (0003.geojson -> 3)
    file_id <- str_extract(basename(f), "\\d+") |> as.integer()

    gdf$file_id <- file_id

    gdf
  }, error = function(e) {
    message("Skipping ", basename(f), ": ", e$message)
    NULL
  })
})

# Remove failed reads
gdfs <- compact(gdfs)

if (length(gdfs) == 0) {
  stop("No valid GeoJSON files could be read.")
}


```

Merge geojsons
```{r}

merged <- bind_rows(gdfs)

cat("Merged", nrow(merged), "features\n")
```

### Kasyo File (for keys)

Key: Basic Traffic Survey Section Number -> Survey Unit Section Number
Left is used by geojson. Right is used in the hourly traffic volume spreadsheet. 
```{r}
roads_counts_kasyo <- read_csv("../shared-svn/projects/matsim-gunma/data/raw/road_counts/mlit/kasyo10.csv", locale = locale(encoding = "CP932")) 

roads_counts_kasyo_key <- roads_counts_kasyo %>% select(longNo = "交通調査基本区間番号...1", shortNo = "交通量／調査単位区間番号", longNoOfStationUpbound = "上り／観測地点交通調査基本区間番号", longNoOfStationDownbound = "下り／観測地点交通調査基本区間番号", longNoOfConnectingRoadStart = "起点側／交通調査基本区間番号", longNoOfConnectingRoadEnd = "終点側／交通調査基本区間番号" )


# upward station and downward station are always the same :)
roads_counts_kasyo_key %>% filter(longNoOfStationUpbound!=longNoOfStationDownbound)


# only looking the actual counting facilities, we only have 857 measuring stations (instead of 2107). However, we will have upward and downward eventually. 4 of these stations are not acutally in our file. So they disappear in the next step.
roads_counts_kasyo_key$longNoOfStationUpbound %>% unique() %>% length()


# there are 853 unique shortNo - longNo combos
roads_counts_kasyo_key_condensed <- roads_counts_kasyo_key %>% filter(longNo == longNoOfStationUpbound)
roads_counts_kasyo_key_condensed %>% pull(longNo) %>% unique() %>% length()
roads_counts_kasyo_key_condensed %>% pull(shortNo) %>% unique() %>% length()


```

SHAPE FILE 
```{r}

tmap_mode("view")

# tm_shape(merged)+tm_lines()



road_counts_shp <- merged %>% 
  separate_wider_position(census,widths = c("Prefecture" = 2,"Unknown1" = 1,"Route" = 5,"Unkown2" = 3),cols_remove = FALSE) %>%
  filter(Prefecture == "10") %>% 
  mutate(longNo = as.numeric(census))%>% 
  inner_join(roads_counts_kasyo_key_condensed, by = c("longNo")) %>% st_as_sf() %>% group_by(shortNo) %>% summarise()


# tm_shape(road_counts_shp) +
#   tm_lines(col = "shortNo")

```

### Road Counts
```{r}
road_counts <- read_csv("../shared-svn/projects/matsim-gunma/data/raw/road_counts/mlit/zkntrf10.csv", locale = locale(encoding = "CP932"))

col_dict <- c(
  "都道府県指定市コード" = "prefecture_code",
  "交通量調査単位区間番号" = "traffic_section_id",
  "道路種別" = "road_type",
  "路線番号" = "route_number",
  "令和３年度調査交通量観測・非観測の別" = "observed_flag",
  "個別調査観測値活用の別" = "individual_observation_flag",
  "１２・２４時間観測の別" = "survey_duration_type",
  "交通量観測年月日" = "survey_date",
  "天候" = "weather",
  "上り・下りの別" = "direction",
  "車種区分" = "vehicle_type",
  "昼間１２時間自動車類交通量（台）" = "traffic_12h_total",
  "２４時間自動車類交通量（台）" = "traffic_24h_total"
)

# Full-width Japanese digits → normal digits
jp_hours <- c("０","１","２","３","４","５","６","７","８","９",
              "１０","１１","１２","１３","１４","１５",
              "１６","１７","１８","１９","２０","２１","２２","２３")

for (h in 0:23) {
  jp_h <- jp_hours[h + 1]
  old_name <- paste0("時間帯別自動車類交通量（台／時）／", jp_h, "時台")
  new_name <- paste0("traffic_", sprintf("%02d", h), "h")
  col_dict[old_name] <- new_name
}

names(road_counts) <- col_dict[names(road_counts)]




# col_dict %>% view()


```
### Analyse Ratio Heavy vs. Light traffic:

```{r}

road_counts_heavy_vs_light <- road_counts %>%
  mutate(shortNo = traffic_section_id) %>% select(shortNo, vehicle_type, vehicle_type,traffic_12h_total, -traffic_section_id) %>%
  group_by(shortNo,vehicle_type) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE)) %>%
  pivot_wider(names_from = vehicle_type, values_from = traffic_12h_total) %>%   mutate(light_vehicle_share = sum(`1`)/sum(`1` + `2`)) %>% select(shortNo,light_vehicle_share)
```



We now take average of upbound/downbound
1: Upbound
2: Downbound

NOTE: some links are only upbound/downbound.
We only examine small vehicles 
1: Small vehicle
2: Large vehicle
```{r}
# road_counts %>% view()

# ONLY FOR SMALL VEHICLES AND IN ONE DIRECTION!
road_counts_merged <- road_counts %>%
  filter(vehicle_type == 1) %>% 
  mutate(shortNo = traffic_section_id) %>% select(shortNo, starts_with("traffic"), -traffic_section_id) %>%
  group_by(shortNo) %>%
  summarise(across(where(is.numeric), mean, na.rm = TRUE), dirs = n()) %>% 
  left_join(road_counts_heavy_vs_light) %>% 
  
  inner_join(road_counts_shp, by = "shortNo") %>% st_as_sf() 

# tm_shape(road_counts_merged) + 
#   tm_lines(col = "traffic_12h_total", palette = "viridis")
```



## MATSim
Read and convert MATSim geometries

 [1] "highway.unclassified"   "highway.residential"    "highway.tertiary"       "highway.cycleway"      
 [5] "highway.secondary"      "highway.trunk"          "highway.primary"        "highway.motorway_link" 
 [9] "highway.trunk_link"     "highway.path"           "highway.secondary_link" "highway.primary_link"  
[13] "highway.service"        "highway.motorway"    
```{r}
# 
# # Read the CSV
# matsim_network_geos_raw <- read.csv("input/v1.6/b3_network-linkGeometries.csv", stringsAsFactors = FALSE)
# 
# # Read MATSim Network, so as to only keep match links that are actually present in the network:
# matsim_cleaned_network <- matsim::read_network("input/v1.6/gunma-v1.6-network.xml.gz")
# 
# ids_matsim_cleaned_network <- matsim_cleaned_network$links %>% 
#   filter(!type %in% c("highway.path","highway.cycleway","highway.residential")) %>%  pull(id)
# 
# # filter geometries to only include those
# 
# matsim_network_geos <- matsim_network_geos_raw %>% filter(LinkId %in% ids_matsim_cleaned_network)
# 
# # Function to convert the Geometry column into a MULTILINESTRING
# parse_multilinestring <- function(geom_str) {
#   # Split by "),(" to separate points
#   coords <- str_extract_all(geom_str, "\\(([^)]+)\\)")[[1]]
#   
#   # Convert each "(x,y)" into numeric vector
#   coords_list <- lapply(coords, function(x) {
#     nums <- str_remove_all(x, "[()]") %>% str_split(",") %>% unlist()
#     as.numeric(nums)
#   })
#   
#   # In this file, each row seems to be a single line (so just wrap as one line)
#   st_multilinestring(list(do.call(rbind, coords_list)))
# }
# 
# # Apply to each row
# matsim_network_geos_sf <- matsim_network_geos %>%
#   rowwise() %>%
#   mutate(geometry = st_sfc(parse_multilinestring(Geometry))) %>%
#   st_as_sf() %>%
#   ungroup()
# 
# st_crs(matsim_network_geos_sf) <- 2450
# 
# saveRDS(matsim_network_geos_sf, "../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf.rds")
# 
# 
# gunma <- st_read("/Users/jakob/git/shared-svn/projects/matsim-gunma/data/raw/01_shapefiles/zzz_deprecated/gunma_2450/gunma_2450.shp")
# matsim_network_geos_sf_filtered <- matsim_network_geos_sf %>% st_filter(gunma)
# 
# saveRDS(matsim_network_geos_sf_filtered, "../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf_filtered.rds")
# 
# 
# matsim_network_geos_sf <- readRDS("../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf.rds")
matsim_network_geos_sf_filtered <- readRDS("../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_network_geos_sf_filtered.rds")



```




# MATCH JARTIC TO MLIT
- Jartic has directionality
- Jartic has historical data which would also be useful (although the point data we purchased is more modern)
- jartic says where exactly the measuring station is, whiel for MLIT the road it shows is huge. 
- MLIT has heavy vs. light traffic



```{r}

tmap_mode("view")
jartic_geolines_filtered <- geo_lines %>% filter(station_id %in% jartic_stations_filtered)
# MLIT: 
tm_shape(road_counts_merged) + tm_lines(col = "traffic_08h", palette = "viridis",lwd = 2) +
  # JARTIC n
  tm_shape(jartic_geolines_filtered) + tm_lines()

jartic_buff <- jartic_geolines_filtered %>% st_buffer(20, endCapStyle = "FLAT")
tm_shape(road_counts_merged) + tm_lines(col = "traffic_08h", palette = "viridis",lwd = 2) +
  # JARTIC n
  tm_shape(jartic_buff) + tm_polygons(col = "red")

    tm_shape(jartic_buff %>% st_filter(road_counts_merged)) + tm_polygons(fill = "red") +
tm_shape(road_counts_merged %>% st_filter(jartic_buff)) + tm_lines() 


```



```{r}

#Find MLIT ids that fit criteria:
# At least 80m of MLIT line should be within buffer (which are 100m long in general)
mlit_to_jartic <- road_counts_merged %>% st_intersection(jartic_buff) %>% mutate(shared_length = as.numeric(st_length(.))) %>%  filter(shared_length >80) %>% select(mlit_id = shortNo, jartic_id = station_id )

# 91 mlit roads, and 157 jartic stations BEFORE manual deletions
length(unique(mlit_to_jartic$mlit_id))
length(unique(mlit_to_jartic$jartic_id))

matched_ids <- unique(mlit_to_jartic$mlit_id)

# matched_ids <- road_counts_merged %>%
#   st_filter(jartic_buff) %>%
#   pull(shortNo) %>%
#   unique()

review_env <- new.env()
review_env$i <- 0


next_match <- function() {
  review_env$i <- review_env$i + 1

  if (review_env$i > length(matched_ids)) {
    message("No more IDs.")
    return(invisible(NULL))
  }

  mlit_id_now <- matched_ids[[review_env$i]]
  jarctic_ids <- mlit_to_jartic %>% filter(mlit_id == mlit_id_now) %>% pull(jartic_id)
  message("Showing ", review_env$i, " / ", length(matched_ids))
  # message("MLIT:", this_id)

  this_line <- road_counts_merged %>% filter(shortNo == mlit_id_now)
  this_buff <- jartic_buff %>% filter(station_id %in% jarctic_ids)
  # this_matsim <- matsim_network_geos_sf_filtered %>% st_filter(this_buff)
  # message("JARTIC: ",   this_buff %>% pull(station_id) %>% paste(collapse = "\n"))

  message(
  paste(
    mlit_id_now,
    this_buff$station_id,
    sep = "\t",
    collapse = "\n"
  )
)

  tm_shape(this_line) +
    tm_lines(col = "black", lwd = 3)+
  tm_shape(this_buff) +
    tm_polygons(fill = "red", fill_alpha = 0.4)
        # tm_shape(this_matsim) + tm_arrows(col = "purple", lwd = 3)

}
```


```{r}
next_match()

```

This is the resulting matching after we did manual checking
```{r}
toRemove = c(15688,11111)

mlit_to_jartic_filtered <- mlit_to_jartic %>% filter(!jartic_id %in% toRemove)

# 89 mlit roads, and 155 jartic stations AFTER manual deletions
length(unique(mlit_to_jartic_filtered$mlit_id))
length(unique(mlit_to_jartic_filtered$jartic_id))
```


# MATCH JARTIC TO MATSIM



Initial Graphic
```{r}

# only use the filtered jartic stations:

geo_points_filtered <- geo_points %>% filter(station_id %in% unique(mlit_to_jartic_filtered$jartic_id))

# make 20m buffer around points
geo_point_buffer <- geo_points_filtered  %>% st_buffer(20)

# tm_shape(matsim_network_geos_sf_filtered) + tm_lines() +
  # tm_shape(merged) + tm_lines(col = "red") +
  # tm_shape(geo_point_buffer) + tm_polygons(fill = "red")
```

find all matsim links that intersect with this buffer:
```{r}
candidates <- geo_point_buffer %>% st_join(matsim_network_geos_sf_filtered) %>% select(station_id,LinkId) %>% st_drop_geometry()

tm_shape(matsim_network_geos_sf_filtered %>% filter(LinkId %in% candidates$LinkId)) + tm_lines() +
  # tm_shape(merged) + tm_lines(col = "red") +
  tm_shape(geo_points_filtered) + tm_dots(fill = "red")
```


function to calculate bearing
```{r}
get_angle <- function(line) {
  coords <- st_coordinates(line)
  p1 <- coords[1, 1:2]
  p2 <- coords[nrow(coords), 1:2]
  atan2(p2[2] - p1[2], p2[1] - p1[1]) * 180 / pi
}
```


calculate angle of matsim links & jartic links:
```{r}
angles_matsim <- matsim_network_geos_sf_filtered %>%
  filter(LinkId %in% candidates$LinkId) %>%   
  mutate(angle_matsim = sapply(geometry, get_angle)) %>% st_drop_geometry() %>% select(LinkId,angle_matsim)
  

angles_jartic <- geo_lines %>% 
  filter(station_id %in% candidates$station_id) %>% 
  mutate(angle_jartic = sapply(geometry, get_angle)) %>% st_drop_geometry() %>%  select(station_id,angle_jartic)

candidates_angles <- candidates %>% left_join(angles_jartic) %>% left_join(angles_matsim)
```


~~filter matches to be maximally 45 degrees apart~~
~~We filtered from 2528 matches to 1040 matches --> we wanna whittle this down to 761~~
We've filtered to the closest angles. 

```{r}
candidates2 <- candidates_angles %>% mutate(angle_diff = abs(angle_jartic - angle_matsim)) %>% group_by(station_id) %>% filter(angle_diff == min(angle_diff)) 

candidates2$station_id %>% unique() %>% length()
candidates2$LinkId %>% unique() %>% length()

tm_shape(matsim_network_geos_sf_filtered %>% filter(LinkId %in% candidates2$LinkId)) + tm_lines() +
  # tm_shape(merged) + tm_lines(col = "red") +
  tm_shape(geo_points) + tm_dots(fill = "red")

```

now lets do a manual review
```{r}

review_env <- new.env()
review_env$i <- 68

matched_ids <- candidates2$station_id


next_match <- function() {
  review_env$i <- review_env$i + 1
  
  if (review_env$i > length(matched_ids)) {
    message("No more IDs.")
    return(invisible(NULL))
  }
  
  jartic_id <- matched_ids[[review_env$i]]
  
  matsim_candidate_ids <- candidates %>%
    filter(station_id == jartic_id) %>%
    pull(LinkId)
  
  matsim_selected_id <- candidates2 %>%
    filter(station_id == jartic_id) %>%
    pull(LinkId)
  
  
  message("Showing ", review_env$i, " / ", length(matched_ids))
  message("JARTIC: ", jartic_id)
  message("Selected MATSim: ", paste(matsim_selected_id, collapse = ", "))
  
  this_dot <- geo_points_filtered %>% filter(station_id == jartic_id)
  this_line <- geo_lines %>% filter(station_id == jartic_id)
  
  this_matsim_candidates <- matsim_network_geos_sf_filtered %>%
    filter(LinkId %in% matsim_candidate_ids)
  
  this_matsim_selected <- matsim_network_geos_sf_filtered %>%
    filter(LinkId %in% matsim_selected_id)
  
# arrow heads
  this_line_end <- this_line %>%
  st_cast("POINT") %>%
  slice_tail(n = 1)

this_matsim_selected_end <- this_matsim_selected %>%
  st_cast("POINT") %>%
  slice_tail(n = 1)

this_matsim_candidates_end <- this_matsim_candidates %>%
  st_cast("POINT") %>%
  group_by(LinkId) %>%
  slice_tail(n = 1)
  
  

bb <- this_line %>%
  st_buffer(100) %>%
  st_bbox()

  # JARCTIC LINES
  tm_shape(this_line) +
  tm_lines(col = "red") + 
  tm_shape(this_line_end) +
  tm_symbols(fill = "red",lwd = 2, size = 0.5) +

  # MATSIM CANDIDATES
  tm_shape(this_matsim_candidates) +
  tm_lines(col = "yellow", lwd = 2, lty = "dashed") +
  tm_shape(this_matsim_candidates_end) + tm_symbols(fill = "yellow",lwd = 2, size = 0.5) +
  tm_shape(this_matsim_selected) +
  # MATSIM SELECTED 
  tm_lines(col = "purple", lwd = 2) +
  tm_shape(this_matsim_selected_end) +
  tm_symbols(fill = "purple", size = 0.5)+
   # JARCTIC CENTER START
  tm_shape(this_dot) +
  tm_symbols(shape = 8,size = 0.5, col = "red") + 
  tm_basemap("OpenStreetMap") +  tm_view(bbox = bb)
}
```


PURPLE = MATSIM LINK
YELLOW = CONTENDERS
RED = JARTIC STATION AND LINK


```{r}
next_match()
```

Questionable:
- #42 (jartic station 10581)
- #44 (jartic station 10692)
- #46 (jartic station 11176)
- #60 (jartic station 5146)
- #75 (jartic station 15214)
- #78 (jartic station 60) --> straight wrong
- #139 (jartic station 1324) --> straight wrong


remove above:
from 155 -> 148
```{r}
jartic_to_mlit_to_matsim <- candidates2 %>% filter(!station_id %in% c(10581,10692,11176,5146,15214,60,1324)) %>% select(jartic_id = station_id, matsim_id = LinkId) %>% left_join(mlit_to_jartic %>% st_drop_geometry())

```


# Putting all together
```{r}

final <- jartic_data_filtered2 %>% 
  select(jartic_id = station_id, hour, hourly_volume) %>%
  right_join(jartic_to_mlit_to_matsim) %>% 
  left_join(road_counts_heavy_vs_light, by = c("mlit_id" = "shortNo")) %>% 
  mutate(hourly_volume_light = hourly_volume * light_vehicle_share) %>% 
  ungroup() %>% 
  select(LinkId = matsim_id, time = hour, count = hourly_volume_light) %>% 
  mutate(time = case_when(time <= 9 ~ paste0("traffic_0",time,"h"), .default = paste0("traffic_",time,"h")))

write_csv(final,"../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_linkId_to_roadcounts_jartic.csv")

```



<!-- There are a couple stations where the same matsim link (LinkID) is matched to multiple jartic stations. For now we will pick the **first** jartic station -->

<!-- added factor of 0.75 to counts to account for freight and commercial traffic . -->
<!-- ```{r} -->

<!-- final <- candidates2 %>% group_by(LinkId) %>%  -->
<!--   summarise(station_id = first(station_id)) %>%  -->
<!--   left_join(data) %>%  -->
<!--   select(LinkId,station_id,time, traffic_volume) %>%  -->
<!--   separate_wider_delim(time, delim = " ", names = c("date","time")) %>%  -->
<!--   filter(date == "2026/01/15") %>%  -->
<!--   separate_wider_delim(time, delim = ":", names = c("hour","minute")) %>%  -->
<!--   group_by(LinkId,hour) %>%  -->
<!--   summarise(hourly_volume = sum(traffic_volume), cnt = n()) %>%  -->
<!--   # group_by(cnt) %>% count() %>% view() -->
<!--   # filter(cnt==12) %>%  -->
<!--   select(LinkId, time = hour, count = hourly_volume) %>% -->
<!--   mutate(time = paste0("traffic_",time,"h")) %>%  -->
<!--   mutate(count = count * 0.75) -->
<!--   # mutate(count = as.double(count)) %>%  -->
<!--   # mutate(count =  sprintf("%.1f", count)) -->

<!-- write_csv(final,"../shared-svn/projects/matsim-gunma/data/processed/roadcounts/matsim_linkId_to_roadcounts_jartic.csv") -->
<!-- ``` -->



