---
title: "telephonebook"
output: html_document
date: "2026-02-02"
---


# Frontmatter

```{r}
library(tidyverse)
library(sf)
library(tmap)
library(purrr)
```


Set inputs and outputs
```{r}
in_facilities_dir <- "../shared-svn/projects/matsim-gunma/data/raw/facility_locations_yellowpages/014000201601/P1B62/"
in_facilities_type <- "../shared-svn/projects/matsim-gunma/data/raw/facility_locations_yellowpages/014000201601/SPEC/TYPECODE.CSV"
in_jis_75_shp <- "../shared-svn/projects/matsim-gunma/data/processed/01_shapefiles/jis_zones/jis_zones_75km_envelope.shp"
out_facilities <- "../shared-svn/projects/matsim-gunma/data/processed/facility_locations_yellowpages/facility_locations_yellowpages.csv"
```

# Meat
Read and translate type codes
```{r}
type_code <- read_csv(in_facilities_type,locale = locale(encoding = "CP932"),col_names = c("type","name_jp"))

type_code_major <- type_code %>% separate_wider_position(type,widths = c("type_major" = 2,"type_minor" = 5)) %>% filter(type_minor == "00000") %>% select(type_major, name_jp) %>% mutate(name_en = c(
  "Fisheries, Agriculture & Forestry",
  "Mining",
  "Construction & Civil Engineering",
  "Food Manufacturing",
  "Textiles",
  "Pulp & Paper",
  "Chemicals & Pharmaceuticals",
  "Petroleum & Coal Products",
  "Rubber Products",
  "Ceramics, Stone & Glass",
  "Iron & Steel",
  "Non-Ferrous Metals",
  "Metal Products",
  "Machinery",
  "Electrical Equipment",
  "Transportation Equipment",
  "Precision Instruments",
  "Other Manufacturing",
  "Commerce",
  "Finance & Insurance",
  "Real Estate",
  "Land Transportation",
  "Marine Transportation",
  "Air Transportation",
  "Warehousing & Logistics",
  "Telecommunications & Information Services",
  "Electricity & Gas",
  "Technical & Professional Services",
  "Sports Facilities",# other
  "Sporting Goods Stores",# other
  "Entertainment & Dining", #other 
  "Tourism & Leisure", # other
  "Hospitals & Welfare",# other
  "Large-Scale Retail Stores",# other
  "Personal & Household Services",
  "Automotive-Related",
  "Education & Learning", #education
  "Government & Public Institutions",
  "Other" # other
))

# type_code_major %>% view()
```


Read JIS zones within 75km of Gunma & determine what prefectures are present
```{r}
jis_75 <- st_read(in_jis_75_shp) %>% 
  st_transform(4612)

prefecture_codes <- jis_75 %>% st_drop_geometry() %>%  separate_wider_position(id, widths = c(id = 2, 3)) %>% pull(id) %>% unique()

```


Read Facilities from yellowpages for each relevant prefecture:
- keep only columns for x,y coordinates and location type
- xform into sf, and check whether it is within the JIS zones file for the 75km envelope

```{r}
locs_raw <- map_dfr(prefecture_codes, function(pref) {
  
  jis_75_for_pref <- jis_75 %>% filter(str_starts(id,pref))

  dir_path <- paste0(in_facilities_dir, pref)

  files <- list.files(dir_path, pattern = "\\.CSV$", full.names = TRUE)

  map_dfr(files, ~ read_csv(
    .x,
    locale = locale(encoding = "CP932"),
    col_names = FALSE,
    col_types = cols(.default = col_character()),
    show_col_types = FALSE
  )) %>%
    select(type = X11, x = X21, y = X22) %>% 
    st_as_sf(coords = c("x","y"), crs = 4612) %>% 
    st_join(jis_75_for_pref, left = FALSE)

})
```

Define whether each facility could be a work, education, or other activity based on the type. 
```{r}
locs_cleaned <- locs_raw %>% 
  separate_wider_position(type,widths = c("type_major" = 2,"type_minor" = 5)) %>% 
  mutate(work = TRUE) %>% 
  mutate(education = type_major == "37") %>% 
  mutate(other = type_major %in% c("29","30","31","32","33","34")) %>% 
  left_join(type_code_major)  %>% 
  st_as_sf()
  # st_as_sf(coords = c("x","y"), crs = 4612)
```


View map and write output csv
```{r}
tmap_mode("view")
locs_cleaned %>% sample_n(10000) %>% tm_shape() + tm_dots(alpha = 0.05)



locs_cleaned %>% st_transform(2450) %>%   mutate(
    x = st_coordinates(geometry)[, 1],
    y = st_coordinates(geometry)[, 2],
  ) %>%  
  select(x,y,work,education,other, type_en = name_en, zone = id) %>%
  st_drop_geometry() %>%
  write_csv(out_facilities)

```

